---
title: "Process and merge stream gage data with JRC/DSWE imagery in California's Central Valley"
fontsize: 8
author: Jessica Walker
date: 7/19/19
output: html_notebook
editor_options:
  chunk_output_type: inline
---
```{r, echo=FALSE}

## ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
## 1_process_and_merge_data.Rmd
## ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
```


```{r, echo = FALSE, include = F, results = 'hide'}

# ---------------------------------------------------------------------- #
####  *********  USER INPUT HERE ***********
# ---------------------------------------------------------------------- #

# Set threshold for maximum percent of no data pixels
nodata_threshold <- 5

# Set files and folders 
# - Output file is written to path.data
path.data <- "C:/temp" #E:/projects/place/data"
file.out <- paste0("merged_", nodata_threshold, "pct.RData")

```


```{r, echo=FALSE, warning=FALSE, message=FALSE}


# ---------------------------------------------------------------------- #
# General setup ####
# ---------------------------------------------------------------------- #

# Load packages
loadPackages <- function(pkgs){
  for (pkg in pkgs){
    if(!require(pkg, character.only = TRUE)){
      install.packages(pkg, dependencies = TRUE)
      require(pkg, character.only = TRUE)
    }
  }
}

loadPackages(c("data.table", # v1.12.0; fread
               "tidyverse")) # v1.2.1 

```


####Workflow 
  - Retrieve Joint Research Commission Monthly Water History v1.0 (JRC) and Dynamic Surface Water Extent (DSWE) 1984-2015 monthly composites in Central Valley HUCs from ScienceBase (Google Drive placeholder)
    - Pre-process data for consistent format, unit conversions, and missing values
    - In scenes with > **`r nodata_threshold`%** No Data, zero out water values pending interpolation
  - Retrieve metadata from NWIS for all Central Valley gages
  - Filter gages for data and temporal requirements
  - Retrieve monthly data from qualifying gages
  - Combine stream gage, JRC, and DSWE data for all HUCs
  
####User actions required
  - Change default directory for output file (**`r path.data`**) if necessary

####Inputs - *All data are retrieved from online sources*
  - JRC monthly composites aggregated by Central Valley HUC 
  - DSWE monthly composites aggregated by Central Valley HUC 
  - NWIS metadata for all Central Valley gages 
  - NWIS monthly records for gages meeting temporal and data requirements

####Output
  - Consolidated file of monthly stream gage, JRC, and DSWE values written to **`r file.path(path.data, file.out)`**


 

```{r, echo = FALSE}

# ---------------------------------------------------------------------- #
#  ------ Function - Process JRC data ---------
# ---------------------------------------------------------------------- #

process_jrc <- function(df, nodata_cap) {
  
  df$date <- as.Date(df$date, format = "%Y-%m-%d")
  
  df <- df %>% 
    slice(-1) %>% # First row is nonsense
    select(date, huc8, nodata = X0, notwater = X1, water = X2)

# Convert from pixels in m^2 to km^2: 900 m^2/pixel x 1e-06 km^2/m^2
  df$water <- df$water * 0.0009  
  df$notwater <- df$notwater * 0.0009  
  df$nodata <- df$nodata * 0.0009  

# Convert "water" --> NA in rows where nodata > x% of the total imaged data
  df$sum <- rowSums(df[, c("nodata", "notwater", "water")], na.rm = T)
  df$pct <- df$nodata/df$sum * 100
  df$water[df$pct > nodata_cap] <- NA

return(df)
  
}

```


```{r,echo = FALSE, message = FALSE, warning = FALSE}

# ---------------------------------------------------------------------- #
#### Get JRC data ####
# ---------------------------------------------------------------------- #

# Get JRC monthly composites within all Central Valley HUCs
# MyDrive/WORK/__PLACE/GEE_output/pekel_monthly_CV_HUC8s_Albers.csv

data_url = "1neHmlcTseqKTlF5tRs38Ruawzua-hCtc"
f.csv <- read.csv(sprintf("https://docs.google.com/uc?id=%s&export=download", data_url))
pk <- process_jrc(f.csv, nodata_threshold)

# Somehow date goes awry
pk$date <- as.Date(pk$date, format = "%Y-%m-%d")
```


```{r, echo = FALSE, message = FALSE, warning = FALSE}

# ---------------------------------------------------------------------- #
# ------ Function - Process DSWE data ------
# ---------------------------------------------------------------------- #

process_dswe <- function(df, nodata_cap) {
  
# X0 = no data, # X1 = not water # X2 = water (high), X3 = water(low conf), X4 = wetland, X5 = water/wetand (low), nodata = clouds, etc., null = no data was present
  colnames(df) <- c("name", 'huc8', "notwater", "water", "water2", "water3", "water4", "nodata", "null", "sqkm")

  df <- df %>% 
    mutate_if(is.factor, as.character) %>%   # Convert name to character
    slice(-1)                                # Remove nonsense 1st row 

# Split name to extract date 
  df$name <- gsub("[[:punct:]]", "", df$name)
  df$name <- gsub("[a-zA-Z ]", "", df$name)
  df$year <- substr(df$name, 1, 4)
  df$month <- substr(df$name, 5, nchar(df$name))

# Convert to date
  df$date <- as.Date(paste(df$year, df$month, "01", sep = "-"), format = "%Y-%m-%d")

# Convert from  pixels to km^2: 1 pixel = 900 m^2 = 0.0009 km^2
  df$notwater <- df$notwater * 0.0009  
  df$nodata <- df$nodata * 0.0009
  df$water <- df$water * 0.0009 
  df$water2 <- df$water2 * 0.0009  
  df$water3 <- df$water3 * 0.0009 
  df$water4 <- df$water4 * 0.0009 
  df$null <- df$null * 0.0009
  
# Convert "water" --> NA in rows where nodata > x% of the total imaged data
# Leaving out 'null' b/c typically that's generated by a missing image
  df$sum <- rowSums(df[, c("nodata", "notwater", "water", "water2", "water3", "water4")], na.rm = T)
  df$pct <- df$nodata/df$sum * 100
  df$water[df$pct > nodata_cap] <- NA
  df$water2[df$pct > nodata_cap] <- NA
  df$water3[df$pct > nodata_cap] <- NA
  df$water4[df$pct > nodata_cap] <- NA
  
# clean up
  df$name <- NULL
  df$year <- NULL
  df$month <- NULL
  df$sqkm <- NULL
  df$null <- NULL

return(df)

}

```


```{r,echo = FALSE, message = FALSE, warning = FALSE}

# ---------------------------------------------------------------------- #
#### Get DSWE data ####
# ---------------------------------------------------------------------- #

# Get DSWE monthly composites across entire CV HUCSs
# my drive/WORK/__PLACE/GEE_output/dswe2_0_monthly_HUC_summaries_1984_2016_hlshd9.csv  17Mar19
data_url = "1yBa-6-YgShQ82vVF4hA4Q3u3lBOADPZb"
f.csv <- read.csv(sprintf("https://docs.google.com/uc?id=%s&export=download", data_url))
ds <- process_dswe(f.csv, nodata_threshold)

```


```{r,echo = FALSE, message = FALSE, warning = FALSE}

# ---------------------------------------------------------------------- #
#### Merge JRC and DSWE data ####
# ---------------------------------------------------------------------- #

# Add columns to JRC data to match DSWE
pk$water2 <- NA
pk$water3 <- NA
pk$water4 <- NA

# Add ID tag to both 
ds$type <-  'dswe'
pk$type <- 'pekel'

# Combine
pk_ds <- rbind(pk, ds)

```


```{r, echo = FALSE, warning=FALSE, message=FALSE, include=FALSE}

# ---------------------------------------------------------------------- #
#### Stream gage - get gage metadata for CV HUCs ####
# ---------------------------------------------------------------------- #

# This step narrows the list of desired gages based on the data available in each

hucs_all <- c('18020002', '18020003','18020004', '18020005', '18020104', '18020111', '18020115',
'18020116', '18020121', '18020122', '18020123', '18020125', '18020126', '18020128', '18020129', '18020151',
'18020152', '18020153', '18020154', '18020155', '18020156', '18020157', '18020158', '18020159', '18020161',
'18020162', '18020163', '18030001', '18030002', '18030003', '18030004', '18030005', '18030006', '18030007',
'18030009', '18030010', '18030012', '18040001', '18040002','18040003', '18040006', '18040007',
'18040008', '18040009', '18040010', '18040011', '18040012', '18040013', '18040014', '18040051')

# Get general info about all gages in Central Valley HUCs from NWIS
site_info <- function(x) {
  df <- fread(sprintf("https://waterservices.usgs.gov/nwis/site/?format=rdb&huc=%s&seriesCatalogOutput=true&siteStatus=all&hasDataTypeCd=dv,aw", x), check.names = FALSE, header=TRUE)
}

# Consolidate all files
g <- do.call(rbind, lapply(hucs_all, site_info))

```



```{r, echo = FALSE, warning = FALSE, message = FALSE}

# ---------------------------------------------------------------------- #
#### Stream gage - set criteria for gage selection ####
# ---------------------------------------------------------------------- #

# Format dates of data retrieval
g$begin_date <- as.Date(g$begin_date, format = "%Y-%m-%d")
g$end_date <- as.Date(g$end_date, format = "%Y-%m-%d")

# Calculate active time for each gage
g$time_active <- g$end_date - g$begin_date

# Only get gages with >= 5 years of data after 1984
# 'Difftime' reported in days but is unreliable as an indication of true data collection period
g.sub <- subset(g, end_date > "1989-01-01" & time_active > 1800 & (parm_cd == '00060' | parm_cd == '00065'))

# Get unique sites
sites <- unique(g.sub$site_no)

# Make sure site names have 8 characters; others aren't recognized in the automatic retrieval URL
sites <- subset(sites, nchar(sites) == 8)

# Make file of info specific to each site: #, HUC#, lat, lon
site_info <- g %>% 
  select(site_no,           # keep select columns; rename
         huc8.sg = huc_cd, 
         lat = dec_lat_va, 
         lon = dec_long_va) %>% 
  as.data.frame(.) %>%      # change to data frame
  slice(-1) %>%             # remove nonsense 1st row
  distinct() %>%            # keep unique rows only
  mutate(lat = as.numeric(lat), 
         lon = as.numeric(lon))
  
```


```{r, echo = FALSE, warning = FALSE, message = FALSE, include = FALSE}

# ---------------------------------------------------------------------- #
#### Stream gage - get data from selected sites ####
# ---------------------------------------------------------------------- #

# Set up holder for all site info  
sg_all <- data.frame()

# Get monthly info from identified stream gages
for (site in sites) {

  file.next <- fread(sprintf("https://waterservices.usgs.gov/nwis/stat/?format=rdb&sites=%s&statReportType=monthly&statTypeCd=all&missingData=on", site), check.names = FALSE, header=TRUE)

  # Ignore no-data files, which start with #
  if (file.next[1, 1] != "#") {
      sg_all <- rbind(sg_all, file.next)
  }
}  

```


```{r, echo = FALSE, warning = FALSE, message = FALSE}

# ---------------------------------------------------------------------- #
#### Stream gage - process aggregated info ####
# ---------------------------------------------------------------------- #

# Data type values are defined here: https://waterservices.usgs.gov/rest/Site-Service.html#outputDataTypeCd
# 00060 = discharge (cu ft/s)

# Remove invalid site numbers
sg <- sg_all[sg_all$site_no %in% sites, ]

# Create date from year and month
sg$date <- as.Date(with(sg, sprintf("%s-%02s-01", year_nu, month_nu)), "%Y-%m-%d")

# Process stream gage data
sg <- sg %>% 
  filter(year_nu > 1983 &
           date < max(pk$date, na.rm = TRUE)) %>%       # Remove dates prior to 1984 and past last imagery date
  mutate(mean_va = as.numeric(mean_va)) %>%             # Ensure values are numbers 
  select(site_no, parameter_cd, mean_va, date) %>% 
  filter(parameter_cd == "00060") %>%                   # Discharge only
  left_join(site_info, by = "site_no") %>%              # Attribute sites with HUC#, lat, lon
  group_by(site_no) %>%                                 # Remove gages in which
      filter(length(unique(mean_va)) > 1) %>%           # - all values are the same
      filter(mean_va >= 0) %>%                          # - gage values are negative
      filter(n() > 60) %>%                              # - < 5 yrs (60 months) of overlapping data exist
  ungroup() %>%                                       # Assign factors   
  mutate(site_no = factor(site_no),
         parameter_cd = factor(parameter_cd),
         huc8.sg = factor(huc8.sg))

```

```{r, echo = FALSE, warning = FALSE, include = FALSE}

# ---------------------------------------------------------------------- #
# Merge imagery and stream gage data across all HUCs####
# ---------------------------------------------------------------------- #

# Merge imagery (JRC/DSWE) and gage data by date. 
pk_ds_sg <-  sg %>% 
   right_join(pk_ds, by = c('date')) %>% 
   rename(huc8.img = huc8) %>%                          # Rename stream gage HUC to avoid confusion between HUCs
   mutate(huc8.img = factor(huc8.img),                  # Force factors
             type = factor(type), 
             site_no = factor(site_no),  
             parameter_cd = factor(parameter_cd)) %>% 
   select(-c(nodata, notwater, sum, pct))               # Delete extraneous columns

# Assign tag for whether imagery water data is interpolated (Y) or original (N)
pk_ds_sg$interp <- ifelse(is.na(pk_ds_sg$water), 'Y', 'N')
pk_ds_sg$interp <- as.factor(pk_ds_sg$interp)

# Make sure all data are valid
pk_ds_sg <-  pk_ds_sg[complete.cases(pk_ds_sg[, 1]), ]

```


```{r, echo = FALSE}

# ---------------------------------------------------------------------- #
# Save file of merged data ####
# ---------------------------------------------------------------------- #

save(pk_ds, pk, ds, pk_ds_sg, file = file.path(path.data, file.out))

```

