---
title: "Plotting stream gage info with JRC and DSWE 2.0 data in California's Central Valley"
fontsize: 9
output: html_notebook
editor_options:
  chunk_output_type: inline
---


```{r, echo=FALSE, warning=FALSE, message=FALSE}

## ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
## 3_plots_gage_discharge_pekel_dswe2_correlations_by_CV_huc.Rmd
## ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

# ---------------------------------------------------------------------- #
#### General setup ####
# ---------------------------------------------------------------------- #

# Load packages in a way that's easy for others to as well
# Credit due: Simon at https://stackoverflow.com/questions/4090169/elegant-way-to-check-for-missing-packages-and-install-them

loadPackages <- function(pkgs){
  for (pkg in pkgs){
    #  require returns TRUE invisibly if it was able to load package
    if(!require(pkg, character.only = TRUE)){
      #  If package was not able to load, re-install
      install.packages(pkg, dependencies = TRUE)
      #  Load package after installing
      require(pkg, character.only = TRUE)
    }
  }
}

# Load packages
loadPackages(c("dataRetrieval", "plyr", "tidyverse", 'data.table', 'knitr', 'kableExtra', 'devtools', 'googledrive', 'zoo'))

# Load mapping packages
loadPackages(c("ggmap", "sf", "maps", "mapdata", 'rgdal', 'plotly'))

# Set default as echo FALSE
knitr::opts_chunk$set(echo = FALSE)


```


```{r, echo = FALSE}

# Plotly setup
Sys.setenv("plotly_username"= "jjwalker")
Sys.setenv("plotly_api_key"="KXnTHoAperT2jUBO89Xr")
```


```{r, echo=FALSE}

# ---------------------------------------------------------------------- #
#### Set correlation threshold and type ####
# ---------------------------------------------------------------------- #

# Identifies threshold between good and bad correlations

cor_threshold <- 0.7

cor_type <-  'pearson' # 'kendall'

```


```{r, echo=FALSE}

# ---------------------------------------------------------------------- #
#### Set NoData threshold ####
# ---------------------------------------------------------------------- #

# This is not dynamic; this identifies which file to load

nodata_threshold <- 5

```


```{r, echo = FALSE, include = F, results = 'hide'}

# ---------------------------------------------------------------------- #
#### Set files and folders ####
# ---------------------------------------------------------------------- #

#plots are saved to path.out/plots

path.data <-  "E:/projects/place"
file.in <- file.path(path.data, "data", paste0("CV_dswe_jrc_gage_", nodata_threshold, "pct_nodata_correlations_", cor_type,".RData"))

# Set path to shapefile directory
shp.dir <- file.path(path.data, "R", "shp")
ifelse(!dir.exists(shp.dir), dir.create(shp.dir), FALSE)

```


```{r, echo=FALSE}

# ---------------------------------------------------------------------- #
#### Load file of processed data ####
# ---------------------------------------------------------------------- #

load(file.in)

```
 

```{r, echo = FALSE, message = FALSE, include = FALSE}

# ---------------------------------------------------------------------- #
#### Download HUC GIS data from Google Drive ####
# ---------------------------------------------------------------------- #

# Download the shapefile if it doesn't exist
  shp.name <- 'WBDHU8_Central_Valley_UTMz10.shp'

if (!file.exists(file.path(shp.dir, shp.name))) {
  data_url = "1_2JnwZFS0blok23-9O7lw-o7Hk96E-nc" 
  download.file(sprintf("https://docs.google.com/uc?id=%s&export=download", data_url), destfile = file.path(shp.dir, "huc.zip"), mode='wb')
  unzip(zipfile = file.path(shp.dir, 'huc.zip'), exdir = shp.dir)
  file.remove(file.path(shp.dir, 'huc.zip'))
}

shp <- st_read(dsn = file.path(shp.dir, shp.name), stringsAsFactors = F)

```


####Background

  - Script **process_gage_discharge_pekel_dswe2_correlations_by_CV_huc.Rmd** must be run prior to this script
  - File of JRC, DSWE, and stream gage monthly values is retrieved

  
  <br>
  
####Central Valley HUCs
  
```{r, echo = FALSE, message = FALSE}

# ---------------------------------------------------------------------- #
#### Plot HUCs shapefile ####
# ---------------------------------------------------------------------- #

shp %>% 
ggplot() + 
  geom_sf(aes(fill = HUC8), show.legend = NA) +  # FALSE for no legend
  theme_bw() +
  coord_sf(crs = st_crs(26910)) # set UTM zone 10 projection

# http://eriqande.github.io/rep-res-web/lectures/making-maps-with-R.html



```
  
  
  
####Difference in proportion of contaminated pixels (DSWE, JRC)

Only values from images with less than **`r nodata_threshold`**% NoData pixels are used in correlations.

####No Data proportions

Pekel and DSWE data show different proportions of NoData pixels (clouds, cloud shadows, or snow). In general, DSWE data have lower proportions of contaminated pixels.

A seasonal breakdown shows that DSWE winter and fall images tend to have more "workable" data than Pekel images. The quality of that data may be substandard, however. 

```{r, echo = F, warning = FALSE}

# ---------------------------------------------------------------------- #
#### Plot boxplot of NoData proportions ####
# ---------------------------------------------------------------------- #

pk_ds_season <- pk_ds
yq <- as.yearqtr(as.yearmon(pk_ds_season$date, "%Y-%m-%d") + 1/12)
pk_ds_season$season <- factor(format(yq, "%q"), levels = 1:4, 
labels = c("Winter", "Spring", "Summer", "Fall"))


ggplot(pk_ds_season, aes(season, pct, color = type)) + 
  geom_boxplot() +
  theme_bw() +
  theme(axis.title.x = element_blank()) + 
  ylab("% NoData pixels") +
  scale_color_discrete(name = "Dataset", breaks = c("dswe", "pekel"), labels = c("DSWE", "JRC"))
```


####Gage:imagery correlations in each HUC  

The _highest_ `r cor_type` correlations between monthly imagery data and monthly streamgage discharge/height data for each respective imagery set in each HUC are below. 

```{r, echo=FALSE, warning=FALSE, message = FALSE, include = FALSE}
  
# ---------------------------------------------------------------------- #
# Display correlation table for JRC and DSWE vs stream gage = TABLE ####
# ---------------------------------------------------------------------- # 

#If the table rather than the plot is displayed, use bolded values are > 0.7.

 cor.huc.max %>%
     select(huc8.img, site_no, parameter_cd, type, cor, n) %>% 
     kable(col.names = c("HUC", "Gage", "Gage type", "Data type", "r", "# months of data"), digits = 3) %>%  
     kable_styling("striped", full_width = FALSE) %>%
     row_spec(c(which(cor.huc.max$cor > cor_threshold)), bold = T) 
```


####Overall number of gages
```{r, echo = FALSE}

pk_ds_sg.int %>%
  ungroup() %>% 
  summarize(n_all = n_distinct(site_no)) %>% 
  
   kable(col.names = c("# of gages")) %>%  
     kable_styling("striped", full_width = FALSE, position = 'left') 
```


####Number of gages under correlation threshold

```{r, echo = FALSE}


# --------------------------------------------------------
# Number of within-HUC correlations above threshold ####
# --------------------------------------------------------

pk_ds_sg.int %>%
  filter(huc8.img == huc8.sg) %>% 
  group_by(type) %>% 
  distinct(huc8.img, cor) %>%
  filter(cor > cor_threshold) %>% 
  summarise(n = n()) %>% 
    
   kable(col.names = c("Dataset", "n > threshold")) %>%  
     kable_styling("striped", full_width = FALSE, position = 'left') 
            

```

####Summary of results for within-HUC max correlations greater than threshold `r cor_threshold`

```{r, echo = FALSE}

cor.huc.max %>% 
  group_by(type) %>%
  filter(cor > cor_threshold) %>% 
  summarize(n = n(),
            pct = n/49*100) %>% 

 kable(col.names = c("Type", "n", "% of HUCs"), digits = 1) %>%  
     kable_styling("striped", full_width = FALSE, position = 'left')  
```
####Range of maximum within-HUC correlations

```{r, echo = FALSE}
# ---------------------------------------------------------------------- #
# Correlation range for MAX corr - JRC and DSWE vs. stream gage ####
# ---------------------------------------------------------------------- #

cor.huc.max %>%
  group_by(type) %>% 
  summarise(min_cor = min(abs(cor)),
            max_cor = max(cor)) %>% 
  kable(col.names = c("Dataset", "Min", "Max"), digits = 3) %>%  
  kable_styling("striped", full_width = FALSE, position = 'left') 



```


####Correlation range in individual HUCs and number of gages
```{r, echo = FALSE}
# ---------------------------------------------------------------------- #
# Correlation range for individual HUCSs ####
# ---------------------------------------------------------------------- #

pk_ds_sg.int %>%
  filter(huc8.img == huc8.sg) %>% 
  distinct(cor, huc8.img, type)  %>% 
  group_by(huc8.img, type) %>% 
  summarise(min_cor = min(abs(cor)),
            max_cor = max(cor),
            n = n()) %>% 
  kable(col.names = c("Dataset", "HUC", "Min", "Max", "# gages"), digits = 3) %>%  
  kable_styling("striped", full_width = FALSE, position = 'left') 


```
####Correlation between COV and R for all correlations

```{r, echo = FALSE}
test <-  pk_ds_sg.int %>%
  group_by(site_no, huc8.img, type, cor) %>% 
  summarise(sd = sd(mean_va),
            mean = mean(mean_va),
            cov = sd/mean)
 # kable(col.names = c("Gage", "Imagery HUC", 'dataset', 'cor', "SD", 'mean', "CV"), digits = 3) %>%  
#  kable_styling("striped", full_width = FALSE, position = 'left') 

cor(test$cor, test$cov)


```
####Summary of gage min/max

```{r, echo = FALSE}
test %>%
  ungroup() %>% 
  summarise(min = min(mean), minSite = site_no[which.min(mean)],
            max = max(mean), maxSite = site_no[which.max(mean)]) %>% 
  kable(col.names = c("Min monthly avg", "Gage #", 'Max monthly avg', 'Gage #'), digits = 3) %>%  
  kable_styling("striped", full_width = FALSE, position = 'left') 



```

####Correlation between covariance in gage discharge and correlation

```{r, echo = FALSE}
test <-  pk_ds_sg.int %>%
  group_by(site_no, huc8.img, type, cor) %>% 
  summarise(sd = sd(mean_va),
            mean = mean(mean_va),
            cov = sd/mean)
 # kable(col.names = c("Gage", "Imagery HUC", 'dataset', 'cor', "SD", 'mean', "CV"), digits = 3) %>%  
#  kable_styling("striped", full_width = FALSE, position = 'left') 

cor(test$cor, test$cov)


```

####Maximum within-HUC correlations for DSWE and JRC
```{r, echo = FALSE, warning=FALSE,  fig.width=8, fig.height=6}

# ---------------------------------------------------------------------- #
# Correlations for JRC and DSWE vs. stream gage - PLOT ####
# ---------------------------------------------------------------------- #

p <- ggplot(cor.huc.max, aes(x = reorder(huc8.img, -cor), y = cor, fill = type)) + 
       geom_bar(stat = 'identity', position = position_dodge()) +
       geom_abline(slope = 0, intercept = cor_threshold, col = "black", lty = 2) +
       theme_bw() +
       theme(axis.text.x = element_text(angle = 80, hjust = 1),
             legend.title = element_blank()) +
       xlab('HUC') +
       ylab('Correlation') +
       scale_fill_manual(name = "Dataset", 
                    values = c('#F8766D', '#00BFC4'), 
                 #   values = c('orange', 'lightblue'),
                    breaks = c("dswe", "pekel"),
                    labels = c("DSWE", "JRC"))

ggplotly(p, tooltip = c('huc8', 'cor')) %>% 
  add_annotations(text="Dataset", xref="paper", yref="paper",
                  x=1.02, xanchor="left",
                  y=0.8, yanchor="bottom",   
                  legendtitle = TRUE, 
                  showarrow = FALSE) %>%
  layout(legend = list(y = 0.8, yanchor = "top"))

```


####Where DSWE or JRC has a better within-HUC correlation

JRC correlations are stronger in almost all HUCs. HUC 18030004 is the only HUC in which no gage matched the requirement of having at least 5 years of overlapping data with the imagery time series. 

```{r, echo = FALSE}

# ---------------------------------------------------------------------- #
#### Spatial plot of whether DSWE or JRC has a higher correlation ####
# ---------------------------------------------------------------------- #

maxes.by.type <- cor.huc.max %>%
    group_by(huc8.img) %>%
    slice(which.max(cor))

tmp <- merge(shp, maxes.by.type, by.x = 'HUC8', by.y = 'huc8.img')

p <- ggplot(tmp) + 
     geom_sf(aes(fill = type)) +
     theme_bw() +
       scale_fill_manual(name = "Imagery with higher\ncorrelation", 
                         #values= c('orange', 'lightblue'), 
                         values = c('#F8766D', '#00BFC4'), 
                         labels = c('DSWE', "JRC")) +
     coord_sf(crs = st_crs(26910)) # set UTM zone 10 projection
p


```

####Months of data available for each best within-HUC correlation
```{r, echo = FALSE, warning = FALSE, message = FALSE }


# ---------------------------------------------------------------------- #
#### Spatial plot of # months available for each 'best' correlation ####
# ---------------------------------------------------------------------- #

n.max <- max(tmp$n)

p <- ggplot(tmp) + 
     geom_sf(aes(fill = n)) +
     theme_bw() +
       scale_fill_gradient(name = "Months of data", limits = c(0, n.max), low = 'lightgreen', high = 'blue') +
     coord_sf(crs = st_crs(26910)) # set UTM zone 10 projection
p
#ggplotly(p)


#chart_link = api_create(p, filename="plot_mos_in_hucs")
#chart_link
```

####Gage:imagery correlation across all HUCs  

Opening up the analysis to all gages, no matter what HUC they're in, reveals that the majority of imagery datasets have a stronger correlation with a gage that is outside that particular HUC (in red). 

```{r, echo = FALSE, warning = FALSE}

# ---------------------------------------------------------------------- #
#### Display gage with max correlation in each HUC - ALL GAGES ####
# ---------------------------------------------------------------------- #

# cor.all.max has the maximum within-huc correlation and the maximum outside-huc correlation for each HUC


t <- cor.all.max %>% 
  group_by(huc8.img, type) %>%
  slice(which.max(cor)) %>% 
  select(huc8.img, site_no, huc8.sg, type, cor, same_huc, n_site)

# Breaking it up like this is necessary b/c kable can't handle the fact that cor.all.max has changed ('select' messes it up)
t %>% 
  kable(col.names = c("HUC - imagery", "Gage w best correlation", "HUC - gage", "Data type", "r", 'Same HUC?','# times gage is best'), digits = 3) %>%
  kable_styling("striped", full_width = FALSE, position = 'left') %>%
  row_spec(c(which(t$cor > cor_threshold)), bold = T) %>%
  row_spec(c(which(t$same_huc == 'N')), color = "red")

```

####Summary of results for all-HUC correlations greater than threshold `r cor_threshold`

```{r, echo = FALSE}

cor.all.max %>% 
  group_by(type) %>%
  filter(cor > cor_threshold) %>% 
  summarize(n = n(),
            pct = n/49*100) %>% 

 kable(col.names = c("Type", "n", "% of HUCs"), digits = 1) %>%  
     kable_styling("striped", full_width = FALSE, position = 'left')  
```

The 'super gage' here is site `r as.character(cor.all.max[which.max(cor.all.max$n_site), 'site_no'])` in HUC `r as.character(cor.all.max[which.max(cor.all.max$n_site), 'huc8.sg'])`


####Super gage 
```{r, echo = FALSE}

# ---------------------------------------------------------------------- #
#### Spatial plot of super gage correlation ####
# ---------------------------------------------------------------------- #

# Get the correlation data into the shapefile
tmp <- merge(shp, cor.all.max, by.x = 'HUC8', by.y = 'huc8.sg')
n_max <- max(tmp$n_site)

# Get the site coordinates
site_coords <- cor.all.max %>% 
               select(site_no, lat,lon, n_site)
site_coords <- site_coords[complete.cases(site_coords),]
#coordinates(site_coords) <-  c('lon', 'lat')

# Transform shp polygons to match WGS84 lat/lon coords
#proj4string(site_coords) <- CRS("+init=epsg:4326")
shp_4326 <- st_transform(shp, '+init=epsg:4326')
tmp_4326 <- st_transform(tmp, '+init=epsg:4326')

# Get hucs that use the super gage
super_hucs <- unique(as.data.frame(tmp[tmp$n_site == n_max, ])['huc8.img'])
super_hucs$huc8.img <- as.character(super_hucs$huc8.img)
tmp1 <- shp_4326 %>% 
     right_join(super_hucs, by = c("HUC8" = 'huc8.img'))

# Plot super gages
ggplot() + 
  geom_sf(data = tmp1, fill = 'red', color = 'gray50', lwd = 0.4)  +
     geom_sf(data = shp_4326, fill = NA, color = 'gray50', lwd = 0.4) +
     geom_point(data = subset(site_coords, n_site == n_max), aes(x = lon, y = lat), color = "black", shape = 18, size = 6) + 
  theme_bw()


```


####Maximum correlations for DSWE and JRC allowing gages in any HUC
```{r, echo = FALSE}

p <- ggplot(t, aes(x = reorder(huc8.img, -cor), y = cor, fill = type)) + 
       geom_bar(stat = 'identity', position = position_dodge()) +
       geom_abline(slope = 0, intercept = cor_threshold, col = "black", lty = 2) +
       theme_bw() +
       theme(axis.text.x = element_text(angle = 80, hjust = 1),
             legend.title = element_blank()) +
       xlab('HUC') +
       ylab('Correlation') +
       scale_fill_manual(name = "Dataset", 
                    values = c('#F8766D', '#00BFC4'), 
                #   values = c('orange', 'lightblue'),
                    breaks = c("dswe", "pekel"),
                    labels = c("DSWE", "JRC"))


ggplotly(p, tooltip = c('huc8', 'cor')) %>% 
  add_annotations(text = "Dataset", xref = "paper", yref = "paper",
                  x=1.02, xanchor="left",
                  y=0.8, yanchor="bottom",   
                  legendtitle = TRUE, 
                  showarrow = FALSE) %>%
  layout(legend = list(y = 0.8, yanchor = "top"))
```



####Correlations between DSWE water categories and gage discharge

Gage discharge and "highest confidence" water extent generally have the highest correlations. 

```{r, echo = FALSE}
 
tmp2 <- ds_sg.cor %>% 
      ungroup(huc8.sg) %>% 
      select(huc8.img, site_no, cor1, cor12, cor123, cor1234, n) %>% #, -huc8.sg)
      group_by(huc8.img) #%>% 
   #   slice(which.max(cor1))

tmp2 %>% 
      kable(col.names = c("HUC", "Site", "r (w1)", "r (w1+w2)", "r (w1+w2+w3)", "r (w1+w2+w3+w4)", "n"), digits = 3) %>%  
      kable_styling("striped", full_width = FALSE, position = 'left') %>%
      row_spec(c(which(tmp2$cor1 > tmp2$cor12)), bold = T)

```
####Which DSWE class combination performs the best?

```{r, echo = FALSE}

 tmp2 %>% 
  ungroup() %>% 
  filter(cor1 > cor1234) %>% 
  summarize(n_cor1 = sum(cor1 > cor12),
            rmse_cor1 = sqrt(mean(cor1 - cor12)^2)
  #          n_cor12 = sum(cor1 < cor12),
  #          rmse_cor12 = sqrt(mean(cor1 - cor12)^2),
            ) %>% 
  kable(col.names = c("# gages where Water > Water1+2", "RMSE"), digits = 3) %>%  
  kable_styling("striped", full_width = FALSE, position = 'left') 
```

```{r, echo = FALSE}
tmp2 %>% 
  ungroup() %>% 
  filter(cor12 > cor1) %>% 
  summarize(n_cor12 = sum(cor1 < cor12),
            rmse_cor12 = sqrt(mean(cor1 - cor12)^2)
            ) %>% 
  kable(col.names = c("# gages where Water < Water1+2", "RMSE"), digits = 3) %>%  
  kable_styling("striped", full_width = FALSE, position = 'left') 

```



####Pekel vs. DSWE correlation

How well do DSWE and JRC/Pekel agree?



####Correlations - JRC vs. DSWE

```{r, echo = FALSE}

# ---------------------------------------------------------------------- #
#### Spatial plot of JRC/DSWE correlations ####
# ---------------------------------------------------------------------- #

tmp <- merge(shp, pk_ds.cor, by.x = 'HUC8', by.y = 'huc8.img')

ggplot(tmp) + 
     geom_sf(aes(fill = cor)) +
     theme_bw() +
       scale_fill_gradient(limits = c(0,1), low = 'green', high = 'blue') +
     coord_sf(crs = st_crs(26910)) # set UTM zone 10 projection
```


####Correlations - DSWE vs. gage
```{r}
# ---------------------------------------------------------------------- #
#### Spatial plot of DSWE/gage correlations ####
# ---------------------------------------------------------------------- #

# Get the max for DSWE by HUC

  tmp2 <- merge(shp, cor.huc.max[cor.huc.max$type == 'dswe', ], by.x = 'HUC8', by.y = 'huc8.img')

  ggplot(tmp2) + 
     geom_sf(aes(fill = cor)) +
     theme_bw() +
     scale_fill_gradient(limits = c(0,1), low = 'green', high = 'blue') +
     coord_sf(crs = st_crs(26910)) # set UTM zone 10 projection

```


####Correlations - JRC vs. gage
```{r, echo = FALSE}

# ---------------------------------------------------------------------- #
#### Spatial plot of JRC/gage correlations ####
# ---------------------------------------------------------------------- #

tmp2 <- merge(shp, cor.huc.max[cor.huc.max$type == 'pekel', ], by.x = 'HUC8', by.y = 'huc8.img')

ggplot(tmp2) + 
     geom_sf(aes(fill = cor)) +
     theme_bw() +
    scale_fill_gradient(limits = c(0,1), low = 'green', high = 'blue') +
     coord_sf(crs = st_crs(26910)) # set UTM zone 10 projection


```


#Where do the DSWE/Pekel correlations (imagery:gage) differ? 

####Absolute differences between DSWE/gage and Pekel/gage r values
```{r, echo = FALSE}

# ---------------------------------------------------------------------- #
#### Spatial plot of Pekel/gage : DSWE/gage correlation differences ####
# ---------------------------------------------------------------------- #
# cor_diffs <- merge(cor_ds_sg_max, cor_pk_sg_max, by = c('huc8', 'parameter_cd'))
# 
# cor_diffs$diff <- abs(cor_diffs$cor.x - cor_diffs$cor.y)
# 
# tmp <- merge(shp, cor_diffs[, c('huc8', 'diff')], by.x = 'HUC8', by.y = 'huc8')
# 
# ggplot(tmp) + 
#      geom_sf(aes(fill = diff)) +
#      theme_bw() +
#      coord_sf(crs = st_crs(26910)) # set UTM zone 10 projection
```



  
```{r, echo = FALSE, warning = FALSE}


#printPlot <- function(df)  {


#
#
# # all imagery data - recorded and interpolated
# pk_ds_sg.all <- subset(pk_ds_sg, huc8 == '18020002' & site_no == 11351945) # & type == 'dswe')
#
# # recorded only
# pk_ds_sg.rec <- pk_ds_sg.all %>% mutate(water = replace(water, which(interp == 'Y'), NA))
#
# # interpolated only
# pk_ds_sg.int <- pk_ds_sg.all %>% mutate(water = replace(water, which(interp == 'N'), NA))
#
# # combine all and recorded
# pk_combined <- rbind(pk_ds_sg.all, pk_ds_sg.rec)
#
# huc.name <- paste0("HUC_", pk_ds_sg.all$huc8[1])
#
#
# # change names
# # thanks, ttps://stackoverflow.com/questions/3472980/ggplot-how-to-change-facet-labels
# imagery.names <-  list('dswe'= "DSWE", 'pekel' = 'JRC/Pekel')
# imagery_labeller <- function(variable,value){
#   return(imagery.names[value])
# }
#
#
# # Plots
# p <- ggplot(pk_ds_sg.all, aes(date, water, group = type)) +
#       geom_line(size = .3, color = 'black') +
#       geom_line(data = pk_ds_sg.int, aes(date, water), color = 'red', size = .8) +
#       geom_point(data = pk_ds_sg.all, aes(date, water, color = interp), size = 0.6) +
# #  geom_line(aes(linetype = type)) +
# #  scale_linetype_manual(values = c(1,1), labels = c("Measured data", "Estimated data")) +
#
#       scale_color_manual(values = c("black", "red"), labels = c("Measured data", "Estimated data")) +
#  #   guides(linetype = guide_legend(override.aes = list(alpha=1))) +
#       theme_bw() +
#       theme(plot.margin=unit(c(1, 1, 1, 1),"cm"),
#         legend.position =  c(0.95, 1.062), #'top',
#         legend.justification = 'right',
#         legend.direction = 'horizontal',
#         legend.title = element_blank()) +
#       xlab("Date") +
#       ylab('Monthly extent (sq km)')  +
#       ggtitle(huc.name) +
#     scale_y_continuous(sec.axis = sec_axis(~.*300, name = "Stream gage discharge\n")) +  # 4.5
#   geom_area(data = pk_ds_sg.all, aes(date, mean_va/300), color = "blue",  alpha = 0.1)
#
#
# p + facet_grid(type ~ ., labeller=imagery_labeller, switch = 'y') +
#    theme(strip.background = element_rect(color="black", fill="white", linetype="solid"))
# +
#
#   # second axis! https://rpubs.com/MarkusLoew/226759
#
#   scale_y_continuous(sec.axis = sec_axis(~.*4.5, name = "Stream gage discharge\n")) +
#   geom_area(data = pk_ds_sg.all, aes(date, mean_va/4.5), color = "blue",  alpha = 0.1)

```


```{r, echo= FALSE, warning = FALSE, message = FALSE, progress_bar = FALSE, fig.height=7, fig.width=8}
# testing

# This can be rewritten such that the pk_ds_sg calls are dropped--the incoming data is already partitioned from that data frame.
# Leaving it for now because it works=

plot_function  <- function(max_cor) {
  
#  km2 <- round(max_cor$km2)
#  plot.x.max <- max(pk_ds_sg.all$date)
#  plot.y.max <- 0.95*max(pk_ds_sg.all$water)
  
  huc_i <- max_cor$huc8.img
  site_i <- max_cor$site_no
  huc_name <- paste0("HUC ", huc_i, ", Site ", site_i)

# all imagery data - recorded and interpolated
  pk_ds_sg.all <- subset(pk_ds_sg.int, huc8.img == huc_i & site_no == site_i)

# recorded only
  pk_ds_sg.rec <- pk_ds_sg.all %>% mutate(water = replace(water, which(interp == 'Y'), NA))

# interpolated only
  pk_ds_sg.int <- pk_ds_sg.all %>% mutate(water = replace(water, which(interp == 'N'), NA))

# combine all and recorded 
  pk_combined <- rbind(pk_ds_sg.all, pk_ds_sg.rec)
 
# change names
# thanks, ttps://stackoverflow.com/questions/3472980/ggplot-how-to-change-facet-labels
  imagery.names <-  list('dswe'= "DSWE", 'pekel' = 'JRC')
  imagery_labeller <- function(variable, value){
    return(imagery.names[value])}

# Plot
  p <- ggplot(pk_ds_sg.all, aes(date, water, group = type)) +  # all
        geom_line(size = .3, color = 'black') +
        geom_line(data = pk_ds_sg.int, aes(date, water), color = 'red', size = .8) +
        geom_point(data = pk_ds_sg.all, aes(date, water, color = interp), size = 0.6) +  #all
        scale_color_manual(values = c("black", "red"), labels = c("Measured data", "Estimated data")) + 
        theme_bw() +
    #    annotate("text", x = as.Date(plot.x.max - 300, '%Y-%m-%d'), y = plot.y.max, label = paste0(km2, " km2")) +
        theme(plot.margin=unit(c(1, 1, 1, 1),"cm"),
          legend.position =  c(0.96, 1.04), #'top', 
          legend.justification = 'right',
          legend.direction = 'horizontal',
          legend.title = element_blank(),
          legend.background = element_rect(fill = NA)) +
        xlab("Date") +
        ylab('Monthly extent (sq km)')  +
        ggtitle(huc_name) +
#   geom_text(data = max_cor, aes(x = plot.x.min, y = plot.y.min - 10, label = site_no), inherit.aes = FALSE) +
#  scale_y_continuous(sec.axis = sec_axis(~.*300, name = "Stream gage discharge\n")) +  # 4.5
#  geom_area(data = pk_ds_sg.all, aes(date, mean_va/300), color = "blue",  alpha = 0.1)

      facet_grid(type ~ ., labeller = imagery_labeller, switch = 'y') +
      theme(strip.background = element_rect(color="black", fill="white", linetype="solid"))

  print(p)

  ggsave(file = file.path(path.data, "plots", paste0("dswe_jrc_huc", huc_i, ".png")), 
        width = 7, 
        height = 5, 
        dpi = 600)

}

```

```{r, echo = FALSE, message = FALSE, warning = FALSE, progress_bar = FALSE}

# ---------------------------------------------------------------------- #
#### Generate all gage::imagery time-series plots
# ---------------------------------------------------------------------- #

#huc_acreage <- shp %>% 
#  distinct(HUC8, km2) %>% 
#  mutate(HUC8 = as.numeric(HUC8))

pk_ds_sg.int %>% 
#    left_join(select(huc_acreage, HUC8, km2), c('huc8.img' = 'HUC8')) %>% #
#    select(-geometry) %>% #
    filter(huc8.sg == huc8.img) %>% 
    group_by(huc8.img) %>% 
    slice(which.max(cor))  %>% 
    do(df.select = plot_function(.)) # 'do' to pass the groups individually; 'df.select' b/c a name is necessary for some reason

```



```{r}
 ggplot(data = pk_ds_sg.int, aes(date, mean_va, group = type)) + 
   scale_fill_manual("Dataset", values = c("blue", "lightblue")) + #, lab#) +
   geom_area(color = 'blue', alpha = 0.1, aes(color = huc8)) + 
   theme_bw() +
   xlab("Date") +
   ylab('Discharge (mean/month)') 
```

