---
title: "Plotting stream gage info with JRC and DSWE 2.0 data in California's Central Valley"
fontsize: 9
output: html_notebook
editor_options:
  chunk_output_type: inline
---


```{r, echo=FALSE, warning=FALSE, message=FALSE}

## ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
## 3_plots_gage_discharge_pekel_dswe2_correlations_by_CV_huc.Rmd
## ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

# ---------------------------------------------------------------------- #
#### General setup ####
# ---------------------------------------------------------------------- #

# Load packages in a way that's easy for others to as well
# Credit due: Simon at https://stackoverflow.com/questions/4090169/elegant-way-to-check-for-missing-packages-and-install-them

loadPackages <- function(pkgs){
  for (pkg in pkgs){
    #  require returns TRUE invisibly if it was able to load package
    if(!require(pkg, character.only = TRUE)){
      #  If package was not able to load, re-install
      install.packages(pkg, dependencies = TRUE)
      #  Load package after installing
      require(pkg, character.only = TRUE)
    }
  }
}

# Load packages
loadPackages(c("dataRetrieval", "plyr", "tidyverse", 'data.table', 'knitr', 'kableExtra', 'devtools', 'googledrive', 'zoo'))

# Load mapping packages
loadPackages(c("ggmap", "sf", "maps", "mapdata", 'rgdal', 'plotly'))

# Set default as echo FALSE
knitr::opts_chunk$set(echo = FALSE)


```


```{r}

# Plotly setup
Sys.setenv("plotly_username"= "jjwalker")
Sys.setenv("plotly_api_key"="KXnTHoAperT2jUBO89Xr")
```

```{r, echo=FALSE}

# ---------------------------------------------------------------------- #
#### Set NoData threshold ####
# ---------------------------------------------------------------------- #

# This is not dynamic; this identifies which file to load

nodata_threshold <- 5

```


```{r, include = F, results = 'hide'}

# ---------------------------------------------------------------------- #
#### Set files and folders ####
# ---------------------------------------------------------------------- #

#plots are saved to path.out/plots

path.data <-  "E:/projects/place"
file.in <- file.path(path.data, "data", paste0("CV_dswe_jrc_data_", nodata_threshold, "_pct_nodata_correlations.RData"))

# Set path to shapefile directory
shp.dir <- file.path(path.data, "R", "shp")
ifelse(!dir.exists(shp.dir), dir.create(shp.dir), FALSE)

```


```{r, echo=FALSE}

# ---------------------------------------------------------------------- #
#### Load file of processed data ####
# ---------------------------------------------------------------------- #

load(file.in)

```
 

```{r, echo  TRUE, message = FALSE, include= FALSE}

# ---------------------------------------------------------------------- #
#### Download HUC GIS data from Google Drive ####
# ---------------------------------------------------------------------- #

# HUCs
filename <- 'WBDHU8_Central_Valley_UTMz10.shp'
data_url = "1_2JnwZFS0blok23-9O7lw-o7Hk96E-nc" 
download.file(sprintf("https://docs.google.com/uc?id=%s&export=download", data_url), destfile = file.path(shp.dir, "huc.zip"), mode='wb')
unzip(zipfile = file.path(shp.dir, 'huc.zip'), exdir = shp.dir)
file.remove(file.path(shp.dir, 'huc.zip'))

shp <- st_read(dsn = file.path(shp.dir, filename), stringsAsFactors = F)
```



####Background

  - Script **process_gage_discharge_pekel_dswe2_correlations_by_CV_huc.Rmd** must be run prior to this script
  - File of JRC (Pekel), DSWE, and stream gage monthly values is retrieved

  
  <br>
  
####Central Valley HUCs
  
```{r}

# ---------------------------------------------------------------------- #
#### Plot HUCs shapefile ####
# ---------------------------------------------------------------------- #

shp %>% 
ggplot() + 
  geom_sf(aes(fill = HUC8), show.legend = NA) +  # FALSE for no legend
  theme_bw() +
  coord_sf(crs = st_crs(26910)) # set UTM zone 10 projection

# http://eriqande.github.io/rep-res-web/lectures/making-maps-with-R.html



```
  
  
  
####Difference in proportion of contaminated pixels (DSWE, Pekel)

Only values from images with less than **`r nodata_threshold`**% NoData pixels are used in correlations.

Prior to applying that standard, Pekel and DSWE data show different proportions of NoData pixels (clouds, cloud shadows, or snow). In general, DSWE data have lower proportions of contaminated pixels.

####No Data proportions

Pekel and DSWE data show different proportions of NoData pixels (clouds, cloud shadows, or snow). In general, DSWE data have lower proportions of contaminated pixels.

A seasonal breakdown shows that DSWE winter and fall images tend to have more "workable" data than Pekel images. The quality of that data may be substandard, however. 

```{r, echo = F, warning = FALSE}

# ---------------------------------------------------------------------- #
#### Plot boxplot of NoData proportions ####
# ---------------------------------------------------------------------- #

pk_ds_season <- pk_ds
yq <- as.yearqtr(as.yearmon(pk_ds_season$date, "%Y-%m-%d") + 1/12)
pk_ds_season$season <- factor(format(yq, "%q"), levels = 1:4, 
labels = c("Winter", "Spring", "Summer", "Fall"))


ggplot(pk_ds_season, aes(season, pct, color = type)) + 
  geom_boxplot() +
  theme_bw() +
  theme(axis.title.x = element_blank()) + 
  ylab("% NoData pixels") +
  scale_color_discrete(name = "Dataset")
```


####Gage:imagery correlations in each HUC  

The _highest_ Pearson correlations between monthly imagery data and monthly streamgage discharge/height data for each respective imagery set in each HUC are below. 

```{r, echo=FALSE, warning=FALSE, message = FALSE, include = FALSE}
  
# ---------------------------------------------------------------------- #
# Display correlation table for Pekel and DSWE vs stream gage = TABLE ####
# ---------------------------------------------------------------------- # 

#If the table rather than the plot is displayed, use Bolded values are > 0.5.

maxes <- cor.huc.max %>%
    select(huc8.img, site_no, parameter_cd, type, cor, -c(interp, n, b, m, huc8.sg)) %>% 
  #  group_by(huc8.img, type) %>%
 #   mutate(n = n()) %>% 
    slice(which.max(cor))

maxes %>%
    select(huc8.img, site_no, parameter_cd, type, cor, n) %>% 
    kable(col.names = c("HUC", "Gage", "Gage type", "Data type", "r", "# months of data"), digits = 3) %>%  
    kable_styling("striped", full_width = FALSE) %>%
    row_spec(c(which(maxes$cor > 0.5)), bold = T) 
```


```{r, echo = FALSE, warning=FALSE,  fig.width=8, fig.height=6}

# ---------------------------------------------------------------------- #
# Display correlations for Pekel and DSWE vs. stream gage - PLOT ####
# ---------------------------------------------------------------------- #

p <- ggplot(maxes, aes(x = reorder(huc8, -cor), y = cor, fill = type)) + 
       geom_bar(stat = 'identity', position = position_dodge()) +
       theme_bw() +
       theme(axis.text.x = element_text(angle = 80, hjust = 1),
             legend.title = element_blank()) +
  xlab('HUC') +
  ylab('Correlation') #+
#  scale_fill_discrete(name = "Dataset")

ggplotly(p, tooltip = c('huc8', 'cor')) %>% 
  add_annotations(text="Dataset", xref="paper", yref="paper",
                  x=1.02, xanchor="left",
                  y=0.8, yanchor="bottom",   
                  legendtitle = TRUE, 
                  showarrow = FALSE) %>%
  layout(legend = list(y = 0.8, yanchor = "top"))

```


####Where DSWE or JRC/Pekel has a better correlation

JRC/Pekel correlations are stronger in almost all HUCs. HUC 18030004 is the only HUC in which no gage matched the requirement of having at least 5 years of overlapping data with the imagery time series. 

```{r, echo = FALSE}

# ---------------------------------------------------------------------- #
#### Spatial plot of whether DSWE or Pekel has a higher correlation ####
# ---------------------------------------------------------------------- #


maxes.by.type <- cor_pdsg %>%
    group_by(huc8) %>%
    slice(which.max(cor))

tmp <- merge(shp, maxes.by.type, by.x = 'HUC8', by.y = 'huc8')

p <- ggplot(tmp) + 
     geom_sf(aes(fill = type)) +
     theme_bw() +
       scale_fill_manual(name = "Imagery with higher correlation", values= c('orange', 'lightblue'), labels = c('DSWE', "JRC/Pekel")) +
     coord_sf(crs = st_crs(26910)) # set UTM zone 10 projection
p



```

####Months of data available for each best correlation
```{r, echo = FALSE, warning = FALSE, message = FALSE }


# ---------------------------------------------------------------------- #
#### Spatial plot of # months available for each 'best' correlation ####
# ---------------------------------------------------------------------- #


maxes.by.type <- cor_pdsg %>%
    group_by(huc8) %>%
    slice(which.max(cor))

tmp <- merge(shp, maxes.by.type, by.x = 'HUC8', by.y = 'huc8')

n.max <- max(tmp$n)

p <- ggplot(tmp) + 
     geom_sf(aes(fill = n)) +
     theme_bw() +
       scale_fill_gradient(name = "Months of data", limits = c(0, n.max), low = 'lightgreen', high = 'blue') +
     coord_sf(crs = st_crs(26910)) # set UTM zone 10 projection
p
#ggplotly(p)


#chart_link = api_create(p, filename="plot_mos_in_hucs")
#chart_link
```


```{r, echo = FALSE}

# ---------------------------------------------------------------------- #
#### Get gage with max correlation in each HUC ####
# ---------------------------------------------------------------------- #

# Looks at gages within HUCs

site_max <- maxes[order(-maxes$cor), ][1, "site_no"][[1]]
site_min <- maxes[order(maxes$cor), ][1, "site_no"][[1]]

cor_max <- maxes[order(-maxes$cor), ][1, "cor"][[1]]
cor_min <- maxes[order(maxes$cor), ][1, "cor"][[1]]

pk_max <-  maxes[order(-maxes$cor), ][1, "type"][[1]]
pk_min <-  maxes[order(-maxes$cor), ][1, "type"][[1]]

huc_max <- maxes[order(-maxes$cor), ][1, "huc8"][[1]]

huc_min <- maxes[order(maxes$cor), ][1, "huc8"][[1]]

sub_max <- subset(pk_ds_sg, site_no == site_max & type == pk_max)

```
####Gage:imagery correlation across all HUCs  

Opening up the analysis to all gages, no matter what HUC they're in, reveals that the majority of imagery datasets have a stronger correlation with a gage that is outside that particular HUC (in red). 

```{r, echo = FALSE, warning = FALSE}

# ---------------------------------------------------------------------- #
#### DIsplay gage with max correlation in each HUC - ALL GAGES ####
# ---------------------------------------------------------------------- #

# Display table of correlations
cor.all.sites %>% 
  kable(col.names = c("HUC - imagery", "Gage w best correlation", "HUC - gage", "Data type", "r", 'Same HUC?','# times gage is best'), digits = 3) %>%  
  kable_styling("striped", full_width = FALSE) %>%
  row_spec(c(which(cor.all.sites$cor > 0.5)), bold = T) %>% 
  row_spec(c(which(cor.all.sites$same_huc=='N')), color = "red")

cor.all.sites <- data.frame(cor.all.sites)
```



The 'super gage' here is site `r as.character(cor.all.sites[which.max(cor.all.sites$n), 'site_no'])` in HUC `r as.character(cor.all.sites[which.max(cor.all.sites$n), 'huc8.y'])`


####Super gage 
```{r, echo = FALSE}

# ---------------------------------------------------------------------- #
#### Spatial plot of super gage correlations ####
# ---------------------------------------------------------------------- #


tmp <- merge(shp, cor.all.sites, by.x = 'HUC8', by.y = 'huc8.y')

n.max <- max(tmp$n)
huc.max <- tmp[tmp$n == 6, "HUC8"][[1]][1]
  
p <- ggplot(tmp) + 
     geom_sf(aes(fill = as.factor(n))) +
    geom_sf(data = shp, fill = NA, color = 'gray50', lwd = 0.4) +
     theme_bw() +
     coord_sf(crs = st_crs(26910)) # set UTM zone 10 projection
p


```


####Correlations between DSWE water categories and gage discharge

Gage discharge and "highest confidence" water extent generally have the highest correlations. 

```{r, echo = FALSE}
 
cor_dsg %>%  
    kable(col.names = c("HUC", "Site", "Data type", "Gage type", "r (w1)", "r (w1+w2)", "r (w1+w2+w3)", "r (w1+w2+w4)", "n"), digits = 3) %>%  
    kable_styling("striped", full_width = FALSE) %>%
    row_spec(c(which(cor_dsg$cor > 0.5)), bold = T)
```




####Pekel vs. DSWE correlation

How well do DSWE and JRC/Pekel agree?



####Correlations - JRC/Pekel vs. DSWE

```{r, echo = FALSE}

# ---------------------------------------------------------------------- #
#### Spatial plot of Pekel/DSWE correlations ####
# ---------------------------------------------------------------------- #

tmp <- merge(shp, cor_pkds, by.x = 'HUC8', by.y = 'huc8')

ggplot(tmp) + 
     geom_sf(aes(fill = cor)) +
     theme_bw() +
       scale_fill_gradient(limits = c(0,1), low = 'green', high = 'blue') +
     coord_sf(crs = st_crs(26910)) # set UTM zone 10 projection
```


####Correlations - DSWE vs. gage
```{r}
# ---------------------------------------------------------------------- #
#### Spatial plot of DSWE/gage correlations ####
# ---------------------------------------------------------------------- #

# Get the max for DSWE by HUC

cor_ds_sg_max <- cor_pdsg %>%
  filter(type == "dswe") %>% 
  group_by(huc8) %>% 
  slice(which.max(cor))

  tmp2 <- merge(shp, cor_ds_sg_max, by.x = 'HUC8', by.y = 'huc8')

ggplot(tmp2) + 
     geom_sf(aes(fill = cor)) +
     theme_bw() +
  scale_fill_gradient(limits = c(0,1), low = 'green', high = 'blue') +
     coord_sf(crs = st_crs(26910)) # set UTM zone 10 projection

```


####Correlations - Pekel vs. gage
```{r, echo = FALSE}

# ---------------------------------------------------------------------- #
#### Spatial plot of Pekel/gage correlations ####
# ---------------------------------------------------------------------- #

cor_pk_sg_max <- cor_pdsg %>%
  filter(type == "pekel") %>% 
  group_by(huc8) %>% 
  slice(which.max(cor))

  tmp <- merge(shp, cor_pk_sg_max, by.x = 'HUC8', by.y = 'huc8')

ggplot(tmp) + 
     geom_sf(aes(fill = cor)) +
     theme_bw() +
    scale_fill_gradient(limits = c(0,1), low = 'green', high = 'blue') +
     coord_sf(crs = st_crs(26910)) # set UTM zone 10 projection


```


Where do the DSWE/Pekel correlations (imagery:gage) differ? 

####Absolute differences between DSWE/gage and Pekel/gage r values
```{r, echo = FALSE}

# ---------------------------------------------------------------------- #
#### Spatial plot of Pekel/gage : DSWE/gage correlation differences ####
# ---------------------------------------------------------------------- #
cor_diffs <- merge(cor_ds_sg_max, cor_pk_sg_max, by = c('huc8', 'parameter_cd'))

cor_diffs$diff <- abs(cor_diffs$cor.x - cor_diffs$cor.y)

tmp <- merge(shp, cor_diffs[, c('huc8', 'diff')], by.x = 'HUC8', by.y = 'huc8')

ggplot(tmp) + 
     geom_sf(aes(fill = diff)) +
     theme_bw() +
     coord_sf(crs = st_crs(26910)) # set UTM zone 10 projection
```



  
```{r, echo = FALSE, warning = FALSE}


#printPlot <- function(df)  {


#
#
# # all imagery data - recorded and interpolated
# pk_ds_sg.all <- subset(pk_ds_sg, huc8 == '18020002' & site_no == 11351945) # & type == 'dswe')
#
# # recorded only
# pk_ds_sg.rec <- pk_ds_sg.all %>% mutate(water = replace(water, which(interp == 'Y'), NA))
#
# # interpolated only
# pk_ds_sg.int <- pk_ds_sg.all %>% mutate(water = replace(water, which(interp == 'N'), NA))
#
# # combine all and recorded
# pk_combined <- rbind(pk_ds_sg.all, pk_ds_sg.rec)
#
# huc.name <- paste0("HUC_", pk_ds_sg.all$huc8[1])
#
#
# # change names
# # thanks, ttps://stackoverflow.com/questions/3472980/ggplot-how-to-change-facet-labels
# imagery.names <-  list('dswe'= "DSWE", 'pekel' = 'JRC/Pekel')
# imagery_labeller <- function(variable,value){
#   return(imagery.names[value])
# }
#
#
# # Plots
# p <- ggplot(pk_ds_sg.all, aes(date, water, group = type)) +
#       geom_line(size = .3, color = 'black') +
#       geom_line(data = pk_ds_sg.int, aes(date, water), color = 'red', size = .8) +
#       geom_point(data = pk_ds_sg.all, aes(date, water, color = interp), size = 0.6) +
# #  geom_line(aes(linetype = type)) +
# #  scale_linetype_manual(values = c(1,1), labels = c("Measured data", "Estimated data")) +
#
#       scale_color_manual(values = c("black", "red"), labels = c("Measured data", "Estimated data")) +
#  #   guides(linetype = guide_legend(override.aes = list(alpha=1))) +
#       theme_bw() +
#       theme(plot.margin=unit(c(1, 1, 1, 1),"cm"),
#         legend.position =  c(0.95, 1.062), #'top',
#         legend.justification = 'right',
#         legend.direction = 'horizontal',
#         legend.title = element_blank()) +
#       xlab("Date") +
#       ylab('Monthly extent (sq km)')  +
#       ggtitle(huc.name) +
#     scale_y_continuous(sec.axis = sec_axis(~.*300, name = "Stream gage discharge\n")) +  # 4.5
#   geom_area(data = pk_ds_sg.all, aes(date, mean_va/300), color = "blue",  alpha = 0.1)
#
#
# p + facet_grid(type ~ ., labeller=imagery_labeller, switch = 'y') +
#    theme(strip.background = element_rect(color="black", fill="white", linetype="solid"))
# +
#
#   # second axis! https://rpubs.com/MarkusLoew/226759
#
#   scale_y_continuous(sec.axis = sec_axis(~.*4.5, name = "Stream gage discharge\n")) +
#   geom_area(data = pk_ds_sg.all, aes(date, mean_va/4.5), color = "blue",  alpha = 0.1)

```


```{r, echo= FALSE, warning = FALSE, message = FALSE, progress_bar = FALSE, fig.height=7, fig.width=8}
# testing

plot_function  <- function(max_cor) {

  huc_i <- max_cor$huc8
  site_i <- max_cor$site_no
  huc_name <- paste0("HUC ", huc_i, ", Site ", site_i)

# all imagery data - recorded and interpolated
  pk_ds_sg.all <- subset(pk_ds_sg, huc8 == huc_i & site_no == site_i)

# recorded only
  pk_ds_sg.rec <- pk_ds_sg.all %>% mutate(water = replace(water, which(interp == 'Y'), NA))

# interpolated only
  pk_ds_sg.int <- pk_ds_sg.all %>% mutate(water = replace(water, which(interp == 'N'), NA))

# combine all and recorded 
  pk_combined <- rbind(pk_ds_sg.all, pk_ds_sg.rec)
 
# change names
# thanks, ttps://stackoverflow.com/questions/3472980/ggplot-how-to-change-facet-labels
  imagery.names <-  list('dswe'= "DSWE", 'pekel' = 'JRC/Pekel')
  imagery_labeller <- function(variable, value){
    return(imagery.names[value])}

  plot.x.min <- min(pk_ds_sg.all$date)
  plot.y.min <- min(pk_ds_sg.all$water)

# Plot
  p <- ggplot(pk_ds_sg.all, aes(date, water, group = type)) + 
        geom_line(size = .3, color = 'black') +
        geom_line(data = pk_ds_sg.int, aes(date, water), color = 'red', size = .8) +
        geom_point(data = pk_ds_sg.all, aes(date, water, color = interp), size = 0.6) +
        scale_color_manual(values = c("black", "red"), labels = c("Measured data", "Estimated data")) + 
        theme_bw() +
        theme(plot.margin=unit(c(1, 1, 1, 1),"cm"),
          legend.position =  c(0.96, 1.04), #'top', 
          legend.justification = 'right',
          legend.direction = 'horizontal',
          legend.title = element_blank(),
          legend.background = element_rect(fill = NA)) +
        xlab("Date") +
        ylab('Monthly extent (sq km)')  +
        ggtitle(huc_name) +
#   geom_text(data = max_cor, aes(x = plot.x.min, y = plot.y.min - 10, label = site_no), inherit.aes = FALSE) +
#  scale_y_continuous(sec.axis = sec_axis(~.*300, name = "Stream gage discharge\n")) +  # 4.5
#  geom_area(data = pk_ds_sg.all, aes(date, mean_va/300), color = "blue",  alpha = 0.1)

      facet_grid(type ~ ., labeller = imagery_labeller, switch = 'y') +
      theme(strip.background = element_rect(color="black", fill="white", linetype="solid"))

  print(p)

  ggsave(file = file.path(path.out, "plots", paste0("dswe_jrc_huc", huc_i, ".png")), 
        width = 7, 
        height = 5, 
        units = "in", 
        dpi = 600)

}

```

```{r, echo = FALSE, message = FALSE, warning = FALSE, progress_bar = FALSE}

# ---------------------------------------------------------------------- #
#### Generate all gage::imagery time-series plots
# ---------------------------------------------------------------------- #

maxes %>% 
    group_by(huc8) %>% 
    slice(which.max(cor)) %>% 
    do(df.select = plot_function(.)) # 'do' to pass the groups individually; 'df.select' b/c a name is necessary for some reason

```





```{r}
 ggplot(data = pk_ds_sg.all, aes(date, mean_va, group = type)) + 
   scale_fill_manual("Dataset", values = c("blue", "lightblue")) + #, lab#) +
   geom_area(color = 'blue', alpha = 0.1, aes(color = huc8)) + 
   theme_bw() +
   xlab("Date") +
   ylab('Discharge (mean/month)') 
```

