---
title: "Correlations of gage info with Pekel and DSWE v1.0 data"
fontsize: 9
output:
  html_document:
    df_print: paged
editor_options:
  chunk_output_type: inline
---
####*All gages in the 50 Central Valley HUCs are queried*

####Workflow  
For all Central Valley HUCs:
* Retrieve compiled Pekel data (JRC Global Surface Monthly Water History) 
* Retrieve compiled DSWE v1.0 data (monthly composites) 
* Clean data
    + Restrict values to those from images with < 10% NoData pixels
* Retrieve stage height and discharge data from all CV stream gages (NWIS)
* Calculate Pearson correlation between gage info and imagery extents


```{r, echo=FALSE, warning=FALSE, message=FALSE}

## correlation_gage ht_discharge_pekel_dswe_all_plots.Rmd


#rm(list=ls())  this is BAD practice apparently

library(dataRetrieval) # USGS data retrieval 
library(ggplot2)
library(tidyr) #lm calc
library(plyr) # mapvalues
library(dplyr) # slicing data
library(data.table) #fread
library(knitr) # format table
library(kableExtra)  #format table
```

```{r, echo=FALSE}

nodata_threshold <- 5

```
NoData threshold is set at r`nodata_threshold`.  That is, only values from images with less than r`nodata_threshold` are used in correlations.

```{r, echo=FALSE}

# ----------------------------------------------
# ------ Function - Process Pekel data ---------
# ----------------------------------------------

process_pekel <- function(f, nodata) {
  
  f$date <- as.Date(df$date, format = "%Y-%m-%d")

# X0 = no data, # X1 = not water # X2 = water
  cols_to_keep <- c("date", "huc8", "X0", "X1", "X2")
  f <- df[, cols_to_keep]
  colnames(f) <- c("date", "huc8", "nodata", "notwater", "water")

# Convert from  # of pixels to km^2: 900 m^2/pixel x 1e-06 km^2/m^2
  f$water <- f$water * 0.0009  
  f$notwater <- f$notwater * 0.0009  
  f$nodata <- f$nodata * 0.0009  

# Convert "water" --> NA in rows where nodata > 1% of the total
  f$sum <- rowSums(f[, c("nodata", "notwater", "water")], na.rm = T)
  f$pct <-f$nodata/f$sum * 100
  f$water[f$pct > nodata] <- NA

return(f)
}

```

```{r,echo=FALSE, message = FALSE, warning = FALSE}

# --------------------------------
# Get Pekel unbuffered data
# ---------------------------------

# Get Pekel monthly composites within all Central Valley HUCs
# MyDrive/WORK/__PLACE/GEE_output/pekel_monthly_CV_HUC8s_Albers.csv

data_url = "1neHmlcTseqKTlF5tRs38Ruawzua-hCtc"
df <- read.csv(sprintf("https://docs.google.com/uc?id=%s&export=download", data_url))
pk <- process_pekel(df, nodata_threshold)

```


```{r, echo=FALSE}

# ----------------------------------------------
# ------ Function - Process DSWE data ---------
# ----------------------------------------------

process_dswe <- function(f, nodata) {
  
# X0 = no data, # X1 = not water # X2 = water
  colnames(f) <- c("huc8", "notwater", "water", "water2", "water3", "nodata", "name")

# prep for substring
  f$name <-  as.character(f$name)
  
#split the name column to extract the data
  f$name <- substr(f$name, 1, nchar(f$name) - 4)
  f.split <- strsplit(f$name, "\\_")
  f <- transform(f, year = sapply(f.split, "[[", 2), month = sapply(f.split, "[[", 3))

## This addition is necessary to flip the order of the files from starting at the 
#  beginning of the year to starting at the end (i.e, file 1 = December).
  f$inverted_month <- plyr::mapvalues(f$month, from = c(seq(1,12)), to = c(seq(12,1)))
  f$month <- f$inverted_month
  f$inverted_month <- NULL
  
# make a date out of it
   f$date <- as.Date(paste(f$year, f$month, "01", sep = "-"), format = "%Y-%m-%d")

# Convert from  m^2 to km^2 1 m^2 = 1e-6 km^2
  f$notwater <- f$notwater * 0.000001  
  f$nodata <- f$nodata * 0.000001
  f$water <- f$water * 0.000001  
  f$water2 <- f$water2 * 0.000001  
  f$water3 <- f$water3 * 0.000001  
  
# Convert "water" --> NA in rows where nodata > x% of the total
  f$sum <- rowSums(f[, c("nodata", "notwater", "water", "water2", "water3")], na.rm = T)
  f$pct <-f$nodata/f$sum * 100
  f$water[f$pct > nodata] <- NA
  f$water2[f$pct > nodata] <- NA
  f$water3[f$pct > nodata] <- NA
  
  #clean up
  f$name <- NULL
  f$year <-  NULL
  f$month <-  NULL

return(f)
}

```

```{r,echo=FALSE, message = FALSE, warning = FALSE}

# ------------------------------
# Get DSWE unbuffered data
# ------------------------------

# Get DSWE monthly composites across entire HUC
# my drive/WORK/__PLACE/data/dswe_cv_huc_data_monthly_composites.csv


data_url = "1ddh13xEPHn2MRWzy0h6qGo5WJz7MTf85"
df <- read.csv(sprintf("https://docs.google.com/uc?id=%s&export=download", data_url))
ds <- process_dswe(df, nodata_threshold)

```


```{r}

# -----------------------------------------------
# Merge Pekel and DSWE data
# -----------------------------------------------


# First Pekel row is nonsense
pk <- pk[-1,]

# Somehow date info goes awry
pk$date <- as.Date(pk$date, format = "%Y-%m-%d")

# Add extra columns to Pekel data
pk$water2 <- NA
pk$water3 <-  NA

# Add extra columns to DSWE
ds$type <-  'dswe'
pk$type <- "pekel"

pk_ds <- rbind(pk, ds)


```



```{r, echo=FALSE, warning=FALSE, message=FALSE, include=FALSE}

# -------------------------------------------------------
# Stream gage - read in gage info (not data) for CV HUCs
# -------------------------------------------------------

# Narrow the list of desired gages based on the data available in each

hucs_all <- c('18020002', '18020003','18020004', '18020005', '18020104', '18020111', '18020115',
'18020116', '18020121', '18020122', '18020123', '18020125', '18020126', '18020128', '18020129', '18020151',
'18020152', '18020153', '18020154', '18020155', '18020156', '18020157', '18020158', '18020159', '18020161',
'18020162', '18020163', '18030001', '18030002', '18030003', '18030004', '18030005', '18030006', '18030007',
'18030009', '18030010', '18030012', '18040001', '18040002','18040003', '18040006', '18040007',
'18040008', '18040009', '18040010', '18040011', '18040012', '18040013', '18040014', '18040051')

# Get general info about all gages in Central Valley HUCs from NWIS
gage_info <- function(x) {
  df <- fread(sprintf("https://waterservices.usgs.gov/nwis/site/?format=rdb&huc=%s&seriesCatalogOutput=true&siteStatus=all&hasDataTypeCd=dv,aw", x), check.names = FALSE, header=TRUE)
}

# Consolidate all files
g <- do.call(rbind, lapply(hucs_all, gage_info))

```


```{r, echo=FALSE, warning=FALSE,message=FALSE}

# ------------------------------------------------
# Stream gage - set criteria for gage selection
# ------------------------------------------------

# Format dates of data retrieval
g$begin_date <- as.Date(g$begin_date, format = "%Y-%m-%d")
g$end_date <- as.Date(g$end_date, format = "%Y-%m-%d")

# Get gages that have an end date past 2010
g.sub <- subset(g, end_date > "2010-01-01")

# Calculate active time for each gage
g.sub$time_active <- g.sub$end_date - g.sub$begin_date

# site_no needs to be a number
g.sub$site_no <- as.numeric(g.sub$site_no)

# Get unique sites
sites <- unique(g.sub$site_no)

# Make sure site names have 8 characters; others aren't recognized in the automatic retrieval URL
sites <- subset(sites, nchar(sites) == 8)

# Make a file with unique sites and corresponding HUC #
site_info <- as.data.frame(g[, c('site_no', 'huc_cd')])
site_info <- site_info[-1,]
site_info <- unique(site_info[c("site_no", "huc_cd")])

```


```{r, echo=FALSE, warning=FALSE, message=FALSE, include=FALSE}

# ---------------------------------------------
# Stream gage - get data from selected sites
# --------------------------------------------

# Set up holder for all site info  
sg <- data.frame()

# Get monthly info from identified stream gages
for (site in sites) {

  file.next <- fread(sprintf("https://waterservices.usgs.gov/nwis/stat/?format=rdb&sites=%s&statReportType=monthly&statTypeCd=all&missingData=on", site), check.names = FALSE, header=TRUE)

  # Ignore no-data files, which start with #
  if (file.next[1, 1] != "#") {
      sg <- rbind(sg, file.next)
  }
}  

# Save a copy
sg.orig <- sg



```


```{r, echo=FALSE, warning=FALSE, message=FALSE}

# ---------------------------------------
# Stream gage - process aggregated info
# ---------------------------------------

# Data type values are defined here: https://waterservices.usgs.gov/rest/Site-Service.html#outputDataTypeCd
# 00060 = discharge (cu ft/s)
# 00065 = gage height (ft)

# Remove sites in which the site# isn't valid
sg <- sg[sg$site_no %in% sites,]

# Create date from year and month columns
sg$date <- as.Date(with(sg, sprintf("%s-%02s-01", year_nu, month_nu)), "%Y-%m-%d")

# Remove dates prior to 1984 and past Pekel data
sg <- subset(sg, year_nu > 1983 & date < max(pk$date, na.rm = TRUE))

# Make sure values aren't characters
sg$mean_va <- as.numeric(sg$mean_va)

# Pare down dataset. This requires sg as a data frame
sg <- data.frame(sg)
cols_to_keep <- c("site_no", "parameter_cd", "mean_va", "date")
sg <- sg[, cols_to_keep]

# Restrict to gage height or discharge info only
sg <- subset(sg, parameter_cd == '00065' | parameter_cd == "00060")

# Replace parameter info
sg[sg$parameter_cd=="00060", "parameter_cd"] <- "discharge"
sg[sg$parameter_cd=="00065", "parameter_cd"] <- "gage ht"

# Attribute sites with HUC#
sg <- merge(sg, site_info, by = "site_no")
colnames(sg)[which(colnames(sg) == "huc_cd")] <- "huc8"

# Remove gages in which 
# - all values are the same
# - gage values are negative
# Assign factors

sg <- sg %>% 
    group_by(site_no) %>%
    filter(length(unique(mean_va)) > 1) %>%
    filter(mean_va >= 0, )
  #  mutate(huc8 = factor(huc8), parameter_cd = factor(parameter_cd)) #this didn't work..!

# Assign factors
sg$site_no <- as.factor(sg$site_no)
sg$parameter_cd <- as.factor(sg$parameter_cd)
sg$huc8 <- as.factor(sg$huc8)

```


```{r, echo=FALSE, warning=FALSE, include=FALSE}

# -----------------------------------------------
# Calculate correlations between gages and imagery
# -----------------------------------------------

# Merge Pekel/DSWE data and gage data
pk_ds_sg <- merge(pk_ds, sg, by = c("date", "huc8"))

# Assign factors 
pk_ds_sg <- pk_ds_sg %>%
      mutate(huc8 = factor(huc8), type = factor(type), site_no = factor(site_no), 
             parameter_cd = factor(parameter_cd))

# Correlations for reduced data set (missing water values are not yet interpolated)
cor_pdsg <- pk_ds_sg %>% 
  dplyr::group_by(huc8, site_no, type, parameter_cd) %>% 
  dplyr::summarize(cor=cor(water, mean_va, use = "pairwise.complete.obs", method = "pearson"),
            n = sum(!is.na(water))) 

# Assign tag for whether Pekel water data is interpolated or original
pk_ds_sg$interp <- ifelse(is.na(pk_ds_sg$water), 'Y', 'N')
pk_ds_sg$interp <- as.factor(pk_ds_sg$interp)
```


The Pearson correlations between monthly imagery data and monthly streamgage discharge/height data for each HUC are below. Bolded values are > 0.5.

####Correlations in each HUC


```{r, echo=FALSE}
  
# -------------------------------------------
# Display correlation table for Pekel and DSWE
# -------------------------------------------


# Attempt to make the higher data type (Pekel or DSWE) red:
# maxes <- cor_psg %>%
#     dplyr::group_by(huc8, site_no, type) %>%
#     dplyr::mutate(
#             the_rank = rank(-cor, ties.method = "random"),
#             cor = cell_spec(cor, color = ifelse(the_rank == 1, 'red', 'black'))) %>%
#     select(huc8, site_no, type, parameter_cd, cor, n)
# 
#     maxes %>%
#     kable(escape = F) %>%
#  #   kable(col.names = c("HUC", "Gage", "Source", "Parameter", "r", "n")) %>%
#     kable_styling("striped", full_width = FALSE)
# 
# # kable(maxes)
  

# original:
maxes <- cor_pdsg %>%
    group_by(huc8)# %>%
 #   slice(which.max(cor))

maxes %>%
    kable(col.names = c("HUC", "Site", "Data type", "Gage type", "r", "n"), digits = 3) %>%  
    kable_styling("striped", full_width = FALSE) %>%
    row_spec(c(which(maxes$cor > 0.5)), bold = T)
```


```{r, echo = FALSE}

# -------------------------------------------
# Get gage with max correlation in each HUC
# -------------------------------------------

site_max <- maxes[order(-maxes$cor), ][1, "site_no"][[1]]
site_min <- maxes[order(maxes$cor), ][1, "site_no"][[1]]

cor_max <- maxes[order(-maxes$cor), ][1, "cor"][[1]]
cor_min <- maxes[order(maxes$cor), ][1, "cor"][[1]]

pk_max <-  maxes[order(-maxes$cor), ][1, "type"][[1]]
pk_min <-  maxes[order(-maxes$cor), ][1, "type"][[1]]

huc_max <- maxes[order(-maxes$cor), ][1, "huc8"][[1]]
huc_min <- maxes[order(maxes$cor), ][1, "huc8"][[1]]

sub_max <- subset(pk_ds_sg, site_no == site_max & type == pk_max)

```

####Correlations between DSWE water categories and gage discharge

Note that adding the 3rd water category doesn't change the correlation appreciably
```{r, echo = FALSE}

# -----------------------------------------------
# Calculate correlations between gages and imagery
# -----------------------------------------------

# Correlations for data set before adding interpolated water values 
# To sum water classes, we need to replace water2 and water3 NAs with 0, so that we can add them to water even if their
# original vlaues is NA
pk_ds_sg[c('water2', 'water3')][is.na(pk_ds_sg[, c('water2', 'water3')])] <- 0  #throws an error if no NA values

# Sum water plus class 2 and class 3
pk_ds_sg$waterplus2 <- rowSums(pk_ds_sg[, c('water', 'water2')]) #, na.rm = TRUE)
pk_ds_sg$waterplus23 <- rowSums(pk_ds_sg[, c('water', 'water2', 'water3')]) #, na.rm = TRUE)

# Calculate correlations
cor_dsg <- pk_ds_sg %>% 
  dplyr::filter(type == 'dswe') %>%
  dplyr::group_by(huc8, site_no, type, parameter_cd) %>% 
  dplyr::summarize(cor = cor(water, mean_va, use = "complete.obs", method = "pearson"),
                   cor2 = cor(waterplus2, mean_va,use = "complete.obs", method = "pearson"),
                   cor3 = cor(waterplus23, mean_va,use = "complete.obs", method = "pearson"),
            n = sum(!is.na(water))) # Used to look at correlation between data density and correlation

cor_dsg %>%
    kable(col.names = c("HUC", "Site", "Data type", "Gage type", "r-water", "r-w1+w2", "r-w1+w2+w3", "n"), digits = 3) %>%  
    kable_styling("striped", full_width = FALSE) %>%
    row_spec(c(which(cor_dsg$cor > 0.5)), bold = T)



```


```{r, echo=FALSE, include = FALSE}

# -----------------------------------------------------
# Get parameter type with max correlation at each gage
# -----------------------------------------------------

# I.e., buffered or unbuffered

max_sites <- cor_psg %>%
    group_by(site_no) %>%
    slice(which.max(cor))

```

```{r, echo = FALSE}

# Save a copy, just in case
pk_ds_sg.original <- pk_ds_sg
```



```{r, echo=FALSE, message=FALSE, include=FALSE}

# --------------------------------------
# Get coefficients for each correlation
# -------------------------------------

# Function to apply linear fit
lm_fit <- function(f) {
  fit <- lm(water ~ mean_va, data = f)
  if (residuals(fit)[1][[1]] > 0 & nrow(f) > 3) {  # necessary to put this in to screen overfit lm's
    f$b <- summary(fit)$coefficients[1, 1]
    f$m <- summary(fit)$coefficients[2, 1]
    }
  return(f)
}



# Calculate correlations for full data set
# Ignore hucs in which all imagery values are NA
pk_ds_sg$b <- 0
pk_ds_sg$m <- 0
pk_ds_sg <- pk_ds_sg %>% 
  group_by(huc8, site_no, type, parameter_cd) %>% 
  filter(sum(is.na(water)) != length(water)) %>%
  do(lm_fit(.))

```

```{r, echo=FALSE}

# ------------------------------------
# Replace NA imagery values with interpolated data
# ------------------------------------

pk_ds_sg$water <- ifelse(is.na(pk_ds_sg$water), pk_ds_sg$mean_va*pk_ds_sg$m + pk_ds_sg$b, pk_ds_sg$water)

```


####Individual correlations

Highest correlation: HUC `r huc_max`, gage `r site_max` (r = `r format(cor_max, digits = 2)`)
```{r, echo=FALSE, warning=FALSE}


ggplot(subset(sub_max, interp == 'N'), aes(mean_va, water)) + 
  geom_point() + #(aes(color= pk_type)) +
  geom_smooth(method = "lm", color = "red", formula = y ~ x, size = 1) +
  theme_bw() + 
  xlab(bquote('Discharge ('~ft^3~s^-1*')')) +
  ylab(bquote('Imagery water extent ('~km^2*')'))

```

