---
title: "Correlations of stream gage info with Pekel and DSWE 2.0 data in California's Central Valley"
fontsize: 9
output: html_notebook
editor_options:
  chunk_output_type: inline
---


####Workflow  
For all 50 HUCs in the Central Valley:

* Retrieve compiled Pekel data (JRC Global Surface Monthly Water History) 
* Retrieve compiled DSWE v2.0 data (monthly composites) 
* Clean data
    + Restrict values to those from images with < 10% NoData pixels
* Retrieve monthly stage height and discharge data from all CV stream gages (NWIS)
* Calculate Pearson correlation between discharge and imagery area of water 
    + In same HUCs
    + In all HUCs



```{r, echo=FALSE, warning=FALSE, message=FALSE}

## ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
## correlation_gage ht_discharge_pekel_dswe_all_plots.Rmd
## ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

# ---------------------------------------------------------------------- #
# General setup ####
# ---------------------------------------------------------------------- #

# Load packages in a way that's easy for others to as well
# Credit due: Simon at https://stackoverflow.com/questions/4090169/elegant-way-to-check-for-missing-packages-and-install-them

loadPackages <- function(pkgs){
  for (pkg in pkgs){
    #  require returns TRUE invisibly if it was able to load package
    if(!require(pkg, character.only = TRUE)){
      #  If package was not able to load, re-install
      install.packages(pkg, dependencies = TRUE)
      #  Load package after installing
      require(pkg, character.only = TRUE)
    }
  }
}

# Load packages
loadPackages(c("dataRetrieval", "plyr", "tidyverse", 'data.table', 'knitr', 'kableExtra', 'devtools', 'googledrive'))

# Load mapping packages
loadPackages(c("ggmap", "sf", "maps", "mapdata", 'rgdal'))

# Set default as echo FALSE
knitr::opts_chunk$set(echo = FALSE)


```

```{r, echo=FALSE}

# ---------------------------------------------------------------------- #
#### Set no data threshold ####
# ---------------------------------------------------------------------- #

nodata_threshold <- 10

```


```{r}

# ---------------------------------------------------------------------- #
#### Set output file ####
# ---------------------------------------------------------------------- #

path.out <-  "D:/projects/place/"
file.out <- paste0("CV_dswe_pekel_data_", nodata_threshold, "_pct_nodata.Rmd")

```


####Geographical Area
```{r, echo = FALSE, message = FALSE, include= FALSE}

# ---------------------------------------------------------------------- #
#### Download HUC GIS data from Google Drive ####
# ---------------------------------------------------------------------- #

# HUCs
filename <- 'WBDHU8_Central_Valley_UTMz10.shp'
data_url = "1_2JnwZFS0blok23-9O7lw-o7Hk96E-nc" 
download.file(sprintf("https://docs.google.com/uc?id=%s&export=download", data_url), destfile = "huc.zip", mode='wb')
unzip(zipfile = 'huc.zip', exdir = "shp")
file.remove('huc.zip')

shp <- st_read(dsn = file.path("D:/projects/place/R/notebooks/shp", filename), stringsAsFactors = F)
```

```{r}

# ---------------------------------------------------------------------- #
#### Plot HUCs shapefile ####
# ---------------------------------------------------------------------- #

shp %>% 
ggplot() + 
  geom_sf(aes(fill = HUC8), show.legend = NA) +  # FALSE for no legend
  theme_bw() +
  coord_sf(crs = st_crs(26910)) # set UTM zone 10 projection

# http://eriqande.github.io/rep-res-web/lectures/making-maps-with-R.html



```


```{r, echo=FALSE}

# ---------------------------------------------------------------------- #
# ------ Function - Process Pekel data ---------
# ---------------------------------------------------------------------- #

process_pekel <- function(df, nodata_cap) {
  
  df$date <- as.Date(df$date, format = "%Y-%m-%d")
  
# First row is nonsense  
  df <- df[-1,]

# X0 = no data, # X1 = not water # X2 = water
  cols_to_keep <- c("date", "huc8", "X0", "X1", "X2")
  df <- df[, cols_to_keep]
  colnames(df) <- c("date", "huc8", "nodata", "notwater", "water")

# Convert from pixels in m^2 to km^2: 900 m^2/pixel x 1e-06 km^2/m^2
  df$water <- df$water * 0.0009  
  df$notwater <- df$notwater * 0.0009  
  df$nodata <- df$nodata * 0.0009  

# Convert "water" --> NA in rows where nodata exceeds <threshold>% of the total
  df$sum <- rowSums(df[, c("nodata", "notwater", "water")], na.rm = T)
  df$pct <- df$nodata/df$sum * 100
  df$water[df$pct > nodata_cap] <- NA

return(df)
}

```


```{r,echo=FALSE, message = FALSE, warning = FALSE}

# ---------------------------------------------------------------------- #
#### Get Pekel unbuffered data ####
# ---------------------------------------------------------------------- #

# Get Pekel monthly composites within all Central Valley HUCs
# MyDrive/WORK/__PLACE/GEE_output/pekel_monthly_CV_HUC8s_Albers.csv

data_url = "1neHmlcTseqKTlF5tRs38Ruawzua-hCtc"
f.csv <- read.csv(sprintf("https://docs.google.com/uc?id=%s&export=download", data_url))
pk <- process_pekel(f.csv, nodata_threshold)

# Somehow date info goes awry
pk$date <- as.Date(pk$date, format = "%Y-%m-%d")
```


```{r, echo=FALSE, message = FALSE, warning = FALSE}

# ---------------------------------------------------------------------- #
# #### Function - Process DSWE data ####
# ---------------------------------------------------------------------- #

process_dswe <- function(df, nodata_cap) {
  
# X0 = no data, # X1 = not water # X2 = water (high), X3 = water(low conf), X4 = wetland, X5 = water/wetand (low)
  colnames(df) <- c("name", 'huc8', "notwater", "water", "water2", "water3", "water4", "nodata", "null", "sqkm")

# Convert name to character
  df <-  df %>% mutate_if(is.factor, as.character) 
  
# First row is useless
  df <- df[-1,]
  
# Split name to extract date
 #  df$name <- substr(df$name, 1, nchar(df$name) - 4)
 #  df.split <- strsplit(df$name, "\\_")
 #  df <- transform(df, year = sapply(df.split, "[[", 2), month = sapply(df.split, "[[", 3))
  
# Split name to extract date 
  df$name <- gsub("[[:punct:]]", "", df$name)
  df$name <- gsub("[a-zA-Z ]", "", df$name)
  df$year <- substr(df$name, 1, 4)
  df$month <- substr(df$name, 5, nchar(df$name))

# Flip the order of the files from starting at the beginning of the year to the end (i.e, file 1 = Dec)
  #df$inverted_month <- plyr::mapvalues(df$month, from = c(seq(1, 12)), to = c(seq(12, 1)))
  #df$month <- df$inverted_month
  #df$inverted_month <- NULL
  
# Convert to date
  df$date <- as.Date(paste(df$year, df$month, "01", sep = "-"), format = "%Y-%m-%d")

# Convert from  m^2 to km^2: 1m^2 = 1e-6 km^2
  # df$notwater <- df$notwater * 0.000001  
  # df$nodata <- df$nodata * 0.000001
  # df$water <- df$water * 0.000001  
  # df$water2 <- df$water2 * 0.000001  
  # df$water3 <- df$water3 * 0.000001  
  # df$water4 <- df$water4 * 0.000001 
  
  
  # Convert from  pixels to km^2: 1 pixel = 900 m^2 = 0.0009 km^2
  df$notwater <- df$notwater * 0.0009  
  df$nodata <- df$nodata * 0.0009
  df$water <- df$water * 0.0009 
  df$water2 <- df$water2 * 0.0009  
  df$water3 <- df$water3 * 0.0009 
  df$water4 <- df$water4 * 0.0009 
  df$null <- df$null * 0.0009
  
  
# Convert "water" --> NA in rows where nodata > x% of the total
# Leaving out 'null' b/c typically that's generated by a missing image
  df$sum <- rowSums(df[, c("nodata", "notwater", "water", "water2", "water3", "water4")], na.rm = T)
  df$pct <- df$nodata/df$sum * 100
  df$water[df$pct > nodata_cap] <- NA
  df$water2[df$pct > nodata_cap] <- NA
  df$water3[df$pct > nodata_cap] <- NA
  df$water4[df$pct > nodata_cap] <- NA
  
# clean up
  df$name <- NULL
  df$year <- NULL
  df$month <- NULL
  df$sqkm <- NULL
  df$null <- NULL

return(df)

}

```


<!-- ```{r,echo=FALSE, message = FALSE, warning = FALSE} -->

<!-- # ---------------------------------------------------------------------- # -->
<!-- #### Get DSWE unbuffered data #### -->
<!-- # ---------------------------------------------------------------------- # -->

<!-- # Get DSWE monthly composites across entire HUC -->
<!-- # my drive/WORK/__PLACE/data/dswe_v2_cv_huc_data_monthly_composites.csv -->
<!-- # my drive/WORK/__PLACE/GEE_output/dswe_monthly_HUC_summaries_1984_2016.csv -->

<!-- data_url = "1hBTBzBh-J-jzbTBYe-X0Tpj3uvNSxpjH" -->
<!-- f.csv <- read.csv(sprintf("https://docs.google.com/uc?id=%s&export=download", data_url)) -->
<!-- ds <- process_dswe(f.csv, nodata_threshold) -->

<!-- ``` -->


<!-- ```{r,echo=FALSE, message = FALSE, warning = FALSE} -->

<!-- # ---------------------------------------------------------------------- # -->
<!-- #### Merge Pekel and DSWE data #### -->
<!-- # ---------------------------------------------------------------------- # -->

<!-- # Add columns to Pekel data to match DSWE -->
<!-- pk$water2 <- NA -->
<!-- pk$water3 <- NA -->
<!-- pk$water4 <- NA -->

<!-- # Add ID tag to both  -->
<!-- ds$type <-  'dswe' -->
<!-- pk$type <- 'pekel' -->

<!-- # Combine -->
<!-- pk_ds <- rbind(pk, ds) -->

<!-- ``` -->

####Difference in proportion of contaminated pixels (DSWE, Pekel)

Only values from images with less than **`r nodata_threshold`**% NoData pixels are used in correlations.


Pekel and DSWE data show different proportions of NoData pixels (clouds, cloud shadows, or snow). In general, DSWE data have lower proportions of contaminated pixels.

#####Boxplot

```{r, echo = F, warning = FALSE}

# ---------------------------------------------------------------------- #
#### Plot boxplot of NoData proportions ####
# ---------------------------------------------------------------------- #

ggplot(pk_ds, aes(type, pct, color = type)) + 
  geom_boxplot() +
  theme_bw() +
  theme(axis.title.x = element_blank()) + 
  ylab("% NoData pixels") +
  scale_color_discrete(name = "Dataset")
```
#####Scatterplot of average percent of NoData pixels (across all HUCs) by date

  
```{r, echo = FALSE, warning = FALSE}

# ---------------------------------------------------------------------- #
#### Scatterplot of NoData proportions over time ####
# ---------------------------------------------------------------------- #

pk_ds %>% 
  group_by(type, date) %>% 
  dplyr::summarize(mean = mean(pct, na.rm = T)) %>% 
  ggplot(., aes(date, mean, group = type, color = type)) + 
  geom_point() + 
  theme_bw() +
  xlab("Date") +
  ylab("Mean % NoData pixels")

```


```{r, echo=FALSE, warning=FALSE, message=FALSE, include=FALSE}

# ---------------------------------------------------------------------- #
#### Stream gage - read in gage info (not data) for CV HUCs ####
# ---------------------------------------------------------------------- #

# Narrow the list of desired gages based on the data available in each

hucs_all <- c('18020002', '18020003','18020004', '18020005', '18020104', '18020111', '18020115',
'18020116', '18020121', '18020122', '18020123', '18020125', '18020126', '18020128', '18020129', '18020151',
'18020152', '18020153', '18020154', '18020155', '18020156', '18020157', '18020158', '18020159', '18020161',
'18020162', '18020163', '18030001', '18030002', '18030003', '18030004', '18030005', '18030006', '18030007',
'18030009', '18030010', '18030012', '18040001', '18040002','18040003', '18040006', '18040007',
'18040008', '18040009', '18040010', '18040011', '18040012', '18040013', '18040014', '18040051')

# Get general info about all gages in Central Valley HUCs from NWIS
gage_info <- function(x) {
  df <- fread(sprintf("https://waterservices.usgs.gov/nwis/site/?format=rdb&huc=%s&seriesCatalogOutput=true&siteStatus=all&hasDataTypeCd=dv,aw", x), check.names = FALSE, header=TRUE)
}

# Consolidate all files
g <- do.call(rbind, lapply(hucs_all, gage_info))

```


```{r, echo=FALSE, warning=FALSE, message=FALSE}

# ---------------------------------------------------------------------- #
#### Stream gage - set criteria for gage selection ####
# ---------------------------------------------------------------------- #

# Format dates of data retrieval
g$begin_date <- as.Date(g$begin_date, format = "%Y-%m-%d")
g$end_date <- as.Date(g$end_date, format = "%Y-%m-%d")

# Get gages that have an end date past 2010
g.sub <- subset(g, end_date > "2010-01-01")

# Calculate active time for each gage
g.sub$time_active <- g.sub$end_date - g.sub$begin_date

# site_no needs to be a number
g.sub$site_no <- as.numeric(g.sub$site_no)

# Get unique sites
sites <- unique(g.sub$site_no)

# Make sure site names have 8 characters; others aren't recognized in the automatic retrieval URL
sites <- subset(sites, nchar(sites) == 8)

# Make file with unique sites and corresponding HUC #
site_info <- as.data.frame(g[, c('site_no', 'huc_cd')])
site_info <- site_info[-1,]
site_info <- unique(site_info[c("site_no", "huc_cd")])

```



```{r}

# ---------------------------------------------------------------------- #
#### Stream gage - create spatial file for plotting ####
# ---------------------------------------------------------------------- #

#site_pts

```





<!-- ```{r, echo=FALSE, warning=FALSE, message=FALSE, include=FALSE} -->

<!-- # ---------------------------------------------------------------------- # -->
<!-- #### Stream gage - get data from selected sites #### -->
<!-- # ---------------------------------------------------------------------- # -->

<!-- # Set up holder for all site info   -->
<!-- sg <- data.frame() -->


<!-- # Get monthly info from identified stream gages -->
<!-- for (site in sites) { -->

<!--   file.next <- fread(sprintf("https://waterservices.usgs.gov/nwis/stat/?format=rdb&sites=%s&statReportType=monthly&statTypeCd=all&missingData=on", site), check.names = FALSE, header=TRUE) -->

<!--   # Ignore no-data files, which start with # -->
<!--   if (file.next[1, 1] != "#") { -->
<!--       sg <- rbind(sg, file.next) -->
<!--   } -->
<!-- }   -->

<!-- # Save a copy -->
<!-- sg.backup <- sg -->

<!-- # Save a file -->
<!-- #write.csv(sg, file = "d:/projects/place/data/tables/sg.csv", row.names = F) -->
<!-- # https://drive.google.com/open?id=1GZv8M9dmT9vH8ccetZTHFI_KOXUbhp04 -->

<!-- ``` -->


<!-- ```{r, echo=FALSE, warning=FALSE, message=FALSE} -->

<!-- # ---------------------------------------------------------------------- # -->
<!-- #### Stream gage - process aggregated info #### -->
<!-- # ---------------------------------------------------------------------- # -->

<!-- # Data type values are defined here: https://waterservices.usgs.gov/rest/Site-Service.html#outputDataTypeCd -->
<!-- # 00060 = discharge (cu ft/s) -->
<!-- # 00065 = gage height (ft) -->

<!-- # Remove invalid site #s -->
<!-- sg <- sg[sg$site_no %in% sites, ] -->

<!-- # Create date from year and month -->
<!-- sg$date <- as.Date(with(sg, sprintf("%s-%02s-01", year_nu, month_nu)), "%Y-%m-%d") -->

<!-- # Remove dates prior to 1984 and past Pekel data -->
<!-- sg <- subset(sg, year_nu > 1983 & date < max(pk$date, na.rm = TRUE)) -->

<!-- # Ensure values are characters -->
<!-- sg$mean_va <- as.numeric(sg$mean_va) -->

<!-- # Pare down datase--this requires sg as a data frame -->
<!-- sg <- data.frame(sg) -->
<!-- cols_to_keep <- c("site_no", "parameter_cd", "mean_va", "date") -->
<!-- sg <- sg[, cols_to_keep] -->

<!-- # Restrict to gage height or discharge info only -->
<!-- sg <- subset(sg, parameter_cd == '00065' | parameter_cd == "00060") -->

<!-- # Replace parameter info -->
<!-- sg[sg$parameter_cd=="00060", "parameter_cd"] <- "discharge" -->
<!-- sg[sg$parameter_cd=="00065", "parameter_cd"] <- "gage ht" -->

<!-- # Attribute sites with HUC# -->
<!-- sg <- merge(sg, site_info, by = "site_no") -->
<!-- colnames(sg)[which(colnames(sg) == "huc_cd")] <- "huc8" -->

<!-- # Remove gages in which  -->
<!-- # - all values are the same -->
<!-- # - gage values are negative -->
<!-- sg <- sg %>%  -->
<!--     group_by(site_no) %>% -->
<!--     filter(length(unique(mean_va)) > 1) %>% -->
<!--     filter(mean_va >= 0) -->

<!-- # Assign factors -->
<!-- sg$site_no <- as.factor(sg$site_no) -->
<!-- sg$parameter_cd <- as.factor(sg$parameter_cd) -->
<!-- sg$huc8 <- as.factor(sg$huc8) -->

<!-- ``` -->


<!-- ```{r, echo=FALSE, warning=FALSE, include=FALSE} -->

<!-- # ---------------------------------------------------------------------- # -->
<!-- # Calculate correlations between imagery and gages in same HUC #### -->
<!-- # ---------------------------------------------------------------------- # -->

<!-- # Merge Pekel/DSWE and gage data -->
<!-- pk_ds_sg <- merge(pk_ds, sg, by = c("date", "huc8")) -->

<!-- # Assign factors  -->
<!-- pk_ds_sg <- pk_ds_sg %>% -->
<!--       mutate(huc8 = factor(huc8), type = factor(type), site_no = factor(site_no),  -->
<!--              parameter_cd = factor(parameter_cd)) -->

<!-- # Correlations for reduced data set (i.e., missing water values are not yet interpolated) -->
<!-- # dplyr explicitly called here b/c plyr doesn't play well with others -->
<!-- cor_pdsg <- pk_ds_sg %>%  -->
<!--   dplyr::group_by(huc8, site_no, type, parameter_cd) %>%  -->
<!--   dplyr::summarize(cor=cor(water, mean_va, use = "pairwise.complete.obs", method = "pearson"), -->
<!--             n = sum(!is.na(water)))  -->

<!-- # Assign tag for whether imagery water data is interpolated (Y) or original (N) -->
<!-- pk_ds_sg$interp <- ifelse(is.na(pk_ds_sg$water), 'Y', 'N') -->
<!-- pk_ds_sg$interp <- as.factor(pk_ds_sg$interp) -->


<!-- # Save a copy -->
<!-- pk_ds_sg.backup <- pk_ds_sg -->
<!-- ``` -->

####Gage:imagery correlations in each HUC  

The _highest_ Pearson correlations between monthly imagery data and monthly streamgage discharge/height data for each HUC are below. Bolded values are > 0.5.

```{r, echo=FALSE}
  
# ---------------------------------------------------------------------- #
# Display correlation table for Pekel and DSWE ####
# ---------------------------------------------------------------------- #

maxes <- cor_pdsg %>%
    group_by(huc8) %>%
    slice(which.max(cor))

maxes %>%
    kable(col.names = c("HUC", "Gage", "Data type", "Gage type", "r", "n"), digits = 3) %>%  
    kable_styling("striped", full_width = FALSE) %>%
    row_spec(c(which(maxes$cor > 0.5)), bold = T)
```


```{r, echo = FALSE}

# ---------------------------------------------------------------------- #
#### Get gage with max correlation in each HUC ####
# ---------------------------------------------------------------------- #

# Looks at gages within HUCs

site_max <- maxes[order(-maxes$cor), ][1, "site_no"][[1]]
site_min <- maxes[order(maxes$cor), ][1, "site_no"][[1]]

cor_max <- maxes[order(-maxes$cor), ][1, "cor"][[1]]
cor_min <- maxes[order(maxes$cor), ][1, "cor"][[1]]

pk_max <-  maxes[order(-maxes$cor), ][1, "type"][[1]]
pk_min <-  maxes[order(-maxes$cor), ][1, "type"][[1]]

huc_max <- maxes[order(-maxes$cor), ][1, "huc8"][[1]]
huc_min <- maxes[order(maxes$cor), ][1, "huc8"][[1]]

sub_max <- subset(pk_ds_sg, site_no == site_max & type == pk_max)

```
####Gage:imagery correlation across all HUCs  

Opening up the analysis to all gages, no matter what HUC they're in, reveals that the majority of imagery datasets have a stronger correlation with a gage that is outside that particular HUC (in red). 

```{r, echo = FALSE, warning = FALSE}

# ---------------------------------------------------------------------- #
#### Get gage with max correlation in each HUC - ALL GAGES ####
# ---------------------------------------------------------------------- #

# Do super gages that correlate well across many different HUCs exist?
# Get the correlations of each site with all HUCs, then look at which site correlates best for each HUC and data type (Pekel, DSWE)

# Calculate max correlations for imagery given info from all possible gages (i.e., not HUC-specific gages)
cor.all <-  sg %>% 
  modify_at('huc8', ~NULL) %>%  # strip out the HUC column from the sg dataset. Only using HUC8 info from IMAGERY
  left_join(pk_ds, by = c('date')) %>%  
  group_by(site_no, huc8, type) %>% 
  summarize(cor = cor(water, mean_va, use = "pairwise.complete.obs", method = "pearson")) %>% 
  group_by(huc8) %>% 
  slice(which.max(cor))

# Join site info from the GAGES back in
# Late Friday I can't figure out a better way to code this join:
sg.slim <- sg %>% distinct(site_no, huc8)
cor.all.sites <- left_join(cor.all, sg.slim, by = c('site_no'), copy = F) 

# Make sure HUC info is just a number
cor.all.sites$huc8.x <-  as.numeric(as.character(cor.all.sites$huc8.x))
cor.all.sites$huc8.y <-  as.numeric(as.character(cor.all.sites$huc8.y))

# Are the gage and imagery in the same HC?
cor.all.sites$same_huc <- 'Y'
cor.all.sites$same_huc[cor.all.sites$huc8.x != cor.all.sites$huc8.y] <- 'N'

# Rearrange table a bit
cor.all.sites <-  cor.all.sites[, c('huc8.x', 'site_no', 'huc8.y', 'type', 'cor', 'same_huc')]

# Get the number of times each gage appears
cor.all.sites <- cor.all.sites %>% group_by(site_no) %>% mutate(n = n())

# Display table of correlations
cor.all.sites %>% 
  kable(col.names = c("HUC - imagery", "Gage w best correlation", "HUC - gage", "Data type", "r", 'Same HUC?', 'n'), digits = 3) %>%  
  kable_styling("striped", full_width = FALSE) %>%
  row_spec(c(which(cor.all.sites$cor > 0.5)), bold = T) %>% 
  row_spec(c(which(cor.all.sites$same_huc=='N')), color = "red")

cor.all.sites <- data.frame(cor.all.sites)


  
```

The 'super gage' here is site `r as.character(cor.all.sites[which.max(cor.all.sites$n), 'site_no'])` in HUC `r as.character(cor.all.sites[which.max(cor.all.sites$n), 'huc8.y'])`





####Super gage 
```{r, echo = FALSE}

# ---------------------------------------------------------------------- #
#### Spatial plot of super gage correlations ####
# ---------------------------------------------------------------------- #


```


####Correlations between DSWE water categories and gage discharge

Gage discharge and "highest confidence" water extent generally have the highest correlations. 

```{r, echo = FALSE, error = FALSE}

# ---------------------------------------------------------------------- #
#### Calculate correlations between gages and all DSWE classes ####
# ---------------------------------------------------------------------- #

# Correlations for data set before adding interpolated water values 
# To sum water classes, we need to replace water2 and water3 NAs with 0, so that we can add them to water
pk_ds_sg[c('water2', 'water3', 'water4')][is.na(pk_ds_sg[, c('water2', 'water3', 'water4')])] <- 0  #throws an error if no NA values

# Sum water plus class 2 and class 3
pk_ds_sg$waterplus2 <- rowSums(pk_ds_sg[, c('water', 'water2')]) 
pk_ds_sg$waterplus23 <- rowSums(pk_ds_sg[, c('water', 'water2', 'water3')]) 
pk_ds_sg$waterplus234 <- rowSums(pk_ds_sg[, c('water', 'water2', 'water3', 'water4')]) 

# Calculate correlations
cor_dsg <- pk_ds_sg %>% 
  dplyr::filter(type == 'dswe') %>%
  dplyr::group_by(huc8, site_no, type, parameter_cd) %>% 
  dplyr::summarize(cor = cor(water, mean_va, use = "complete.obs", method = "pearson"),
                   cor2 = cor(waterplus2, mean_va,use = "complete.obs", method = "pearson"),
                   cor3 = cor(waterplus23, mean_va,use = "complete.obs", method = "pearson"),
                   cor4 = cor(waterplus234, mean_va,use = "complete.obs", method = "pearson"),
            n = sum(!is.na(water))) 

# Display nicely
cor_dsg <- cor_dsg %>%
    group_by(huc8) %>% 
    slice(which.max(cor)) 
 
cor_dsg %>%  
    kable(col.names = c("HUC", "Site", "Data type", "Gage type", "r (w1)", "r (w1+w2)", "r (w1+w2+w3)", "r (w1+w2+w3+w4)", "n"), digits = 3) %>%  
    kable_styling("striped", full_width = FALSE) %>%
    row_spec(c(which(cor_dsg$cor > 0.5)), bold = T)



```


```{r, echo=FALSE, message=FALSE, include=FALSE}

# ---------------------------------------------------------------------- #
#### Get coefficients for each correlation ####
# ---------------------------------------------------------------------- #

# Function to apply linear fit
lm_fit <- function(f) {
  print(head(f))
  fit <- lm(water ~ mean_va, data = f)
  results <- broom::tidy(fit)
  f$b <- results$estimate[1]
  f$m <- results$estimate[2]
#  if (residuals(fit)[1][[1]] > 0 & nrow(f) > 3) {  # necessary to put this in to screen overfit lm's...sometimes
    #   }
  return(f)
}


# Calculate correlations; ignore hucs in which all imagery values are NA
pk_ds_sg$b <- 0
pk_ds_sg$m <- 0
pk_ds_sg <- pk_ds_sg %>% 
  group_by(huc8, site_no, type, parameter_cd) %>% 
  filter(sum(is.na(water)) != length(water)) %>%
  do(lm_fit(.))
  

```


```{r, echo=FALSE}
# ---------------------------------------------------------------------- #
#### Replace NA imagery values with interpolated data ####
# ---------------------------------------------------------------------- #

pk_ds_sg$water <- ifelse(is.na(pk_ds_sg$water), pk_ds_sg$mean_va*pk_ds_sg$m + pk_ds_sg$b, pk_ds_sg$water)

```


####Individual correlations

Highest correlation: HUC `r huc_max`, gage `r site_max` (r = `r format(cor_max, digits = 2)`)
```{r, echo=FALSE, warning=FALSE}
# ---------------------------------------------------------------------- #

# ---------------------------------------------------------------------- #


ggplot(subset(sub_max, interp == 'N'), aes(mean_va, water)) + 
  geom_point() + #(aes(color= pk_type)) +
  geom_smooth(method = "lm", color = "red", formula = y ~ x, size = 1) +
  theme_bw() + 
  xlab(bquote('Discharge ('~ft^3~s^-1*')')) +
  ylab(bquote('Imagery water extent ('~km^2*')'))

```
####Pekel vs. DSWE correlations


```{r, echo = F}

# ---------------------------------------------------------------------- #
#### Get Pekel/DSWE correlations ####
# ---------------------------------------------------------------------- #

pk.sub <- pk[, c('date', 'water', 'huc8')]
colnames(pk.sub)[2] <- 'water_pk'

ds.sub <- ds[, c('date', 'water', 'huc8')]
colnames(ds.sub)[2] <- 'water_ds'

pk_ds.sub <- merge(pk.sub, ds.sub, by = c('date', 'huc8'))

# Calculate correlations
cor_pkds <- pk_ds.sub %>% 
  dplyr::group_by(huc8) %>% 
  dplyr::summarize(cor = cor(water_pk, water_ds, use = "complete.obs", method = "kendall"), 
            n_pekel = sum(!is.na(water_pk)),
            n_dswe = sum(!is.na(water_ds))) # Used to look at correlation between data density and correlation

cor_pkds %>%
    kable(col.names = c("HUC", "r", 'n (Pekel)', 'n (DSWE)'), digits = 3) %>%  
    kable_styling("striped", full_width = FALSE) %>%
    row_spec(c(which(cor_pkds$cor > 0.5)), bold = T)



```

Is there any spatial pattern to the correlations?  


####Pekel vs. DSWE correlations  

Where do the two imagery datasets agree/disagree?
```{r, echo = FALSE}

# ---------------------------------------------------------------------- #
#### Spatial plot of Pekel/DSWE correlations ####
# ---------------------------------------------------------------------- #

tmp <- merge(shp, cor_pkds, by.x = 'HUC8', by.y = 'huc8')

ggplot(tmp) + 
     geom_sf(aes(fill = cor)) +
     theme_bw() +
       scale_fill_gradient(limits = c(0,1), low = 'green', high = 'blue') +
     coord_sf(crs = st_crs(26910)) # set UTM zone 10 projection
```

####DSWE vs. gage correlations  
```{r}
# ---------------------------------------------------------------------- #
#### Spatial plot of DSWE/gage correlations ####
# ---------------------------------------------------------------------- #

# Get the max for each type (Pekel, DSWE) by HUC

cor_ds_sg_max <- cor_pdsg %>%
  filter(type == "dswe") %>% 
  group_by(huc8) %>% 
  slice(which.max(cor))

  tmp2 <- merge(shp, cor_ds_sg_max, by.x = 'HUC8', by.y = 'huc8')

ggplot(tmp2) + 
     geom_sf(aes(fill = cor)) +
     theme_bw() +
  scale_fill_gradient(limits = c(0,1), low = 'green', high = 'blue') +
     coord_sf(crs = st_crs(26910)) # set UTM zone 10 projection

```

####Pekel vs. gage correlations 
```{r, echo = FALSE}

# ---------------------------------------------------------------------- #
#### Spatial plot of Pekel/gage correlations ####
# ---------------------------------------------------------------------- #

cor_pk_sg_max <- cor_pdsg %>%
  filter(type == "pekel") %>% 
  group_by(huc8) %>% 
  slice(which.max(cor))

  tmp <- merge(shp, cor_pk_sg_max, by.x = 'HUC8', by.y = 'huc8')

ggplot(tmp) + 
     geom_sf(aes(fill = cor)) +
     theme_bw() +
     coord_sf(crs = st_crs(26910)) # set UTM zone 10 projection


```

Where do the DSWE/Pekel correlations (imagery:gage) differ? 

####Absolute differences between DSWE/gage and Pekel/gage r values
```{r, echo = FALSE}

# ---------------------------------------------------------------------- #
#### Spatial plot of Pekel/gage : DSWE/gage correlation differences ####
# ---------------------------------------------------------------------- #
cor_diffs <- merge(cor_ds_sg_max, cor_pk_sg_max, by = c('huc8', 'parameter_cd'))

cor_diffs$diff <- abs(cor_diffs$cor.x - cor_diffs$cor.y)

tmp <- merge(shp, cor_diffs[, c('huc8', 'diff')], by.x = 'HUC8', by.y = 'huc8')

ggplot(tmp) + 
     geom_sf(aes(fill = diff)) +
     theme_bw() +
     coord_sf(crs = st_crs(26910)) # set UTM zone 10 projection
```

```

