---
title: "Pekel data vs gage data"
output: html_notebook
fontsize: 9
editor_options: 
  chunk_output_type: inline
---

###Buffered/non-buffered streams; gage height/discharge
```{r, echo=FALSE, warning=FALSE}

# huc8_Pekel_discharge vs height and buffer vs nonbuffer

huc_num <- "18020115" # 18020116


```
Here we use stream gage data to fill gaps in the coincident Pekel JRC Global Surface Water timeseries.  

  * Monthly data are used in both cases, limited to **HUC`r huc_num`**.  
  * 4-way comparison:
    + Discharge data vs. unbuffered data
    + Discharge data vs. buffered data
    + Gage height vs. unbuffered data
    + Gage height vs. buffered data

where 'buffered' data are Pekel data limited to 500m around each stream.
```{r, echo=FALSE, warning=FALSE}

library(dataRetrieval) # USGS data retrieval 
library(ggplot2)
library(tidyr) #lm calc
library(dplyr) # slicing data
library(data.table) #fread
library(sf) #shapefile
library(knitr) # format table
library(kableExtra)  #format table

```
#####**Max monthly water extent - Pekel data for entire HUC**

```{r,echo=FALSE}

# --------------------------------
# Pekel - unbuffered data
# ---------------------------------

# Get Pekel monthly composites within all Central Valley HUCs
# my drive/WORK/__PLACE/GEE_output/pekel_monthly_CV_HUC8s.csv

data_url = "1JuFS2f1SLqqdDajgisU_BDnb_FLfSvU7"
df <- read.csv(sprintf("https://docs.google.com/uc?id=%s&export=download", data_url))

# Format data
pk_u <- df
pk_u$date <- as.Date(pk_u$date, format = "%Y-%m-%d")

# X0 = no data, # X1 = not water # X2 = water
cols_to_keep <- c("date", "huc8", "X2")
pk_u <- pk_u[, cols_to_keep]

pk_u$X2 <- pk_u$X2 * 0.0009   # convert from  #pixels to km^2: 900 m^2/pixel x 1e-06 km^2/m^2
colnames(pk_u)[which(colnames(pk_u)=="X2")] <- "water"
pk_u <- subset(pk_u, huc8 == huc_num)
```

```{r, echo=FALSE, warning=FALSE}

pk_u_line <- 10 #192

ggplot(pk_u, aes(date, water)) + 
  geom_line() + 
  geom_point() +
  theme_bw() +
  xlab("Date") +
  ylab(bquote('Water extent ('~km^2*')')) +
  geom_hline(color = 'red', linetype = "dashed", yintercept = pk_u_line)
```

#####**Max monthly water extent - Pekel data limited to 500m buffered streams**

```{r, echo=FALSE, warning=FALSE}

# ------------------------------
# Pekel - buffered data
# ------------------------------

# Get Pekel monthly composites within 500m of streams in CV hucs
# my drive/WORK/__PLACE/GEE_output/pekel_monthly_CV_HUC8s_500m_streams.csv

data_url = "1amcdHV9V3DXsS_fAgBMvX7E1WhZMyiKm"
df <- read.csv(sprintf("https://docs.google.com/uc?id=%s&export=download", data_url))

# Format data
pk_b <- df
pk_b$date <- as.Date(pk_b$date, format = "%Y-%m-%d")

# X0 = no data, # X1 = not water # X2 = water
cols_to_keep <- c("date", "huc8", "X2")
pk_b <- pk_b[, cols_to_keep]

pk_b$X2 <- pk_b$X2 * 0.0009   # convert from  #pixels to km^2: 900 m^2/pixel x 1e-06 km^2/m^2
colnames(pk_b)[which(colnames(pk_b)=="X2")] <- "water"
pk_b <- subset(pk_b, huc8 == huc_num)
```

```{r, echo=FALSE, warning=FALSE}

pk_b_line <- 10 #55

ggplot(pk_b, aes(date, water)) + 
  geom_line() + 
  geom_point() +
  theme_bw() +
  xlab("Date") +
  ylab(bquote('Water extent ('~km^2*')')) +
  geom_hline(color = 'red', linetype = "dashed", yintercept = pk_b_line)
```
Given the noise in each time series, all data below the dashed red lines are simply removed and replaced with NA. (Should eventually be replaced by a more sophisticated noise removal process).

#####**Cleaned-up plot for entire HUC**

```{r, echo=FALSE, warning=FALSE}

pk_u$water[which(pk_u$water < pk_u_line)] <- NA


ggplot(pk_u, aes(date, water)) + 
  geom_line() + 
  geom_point() +
  theme_bw() +
  xlab("Date") +
  ylab(bquote('Water extent ('~km^2*')')) +
  geom_hline(color = 'red', linetype = "dashed", yintercept = pk_u_line)
```

#####**Cleaned-up plot for buffered HUC**

```{r, echo=FALSE, warning=FALSE}

pk_b$water[which(pk_b$water < pk_b_line)] <- NA


ggplot(pk_b, aes(date, water)) + 
  geom_line() + 
  geom_point() +
  theme_bw() +
  xlab("Date") +
  ylab(bquote('Water extent ('~km^2*')')) +
  geom_hline(color = 'red', linetype = "dashed", yintercept = pk_b_line)
```
The plots show some differences in slope up until ~1995, but generally track each other well.

```{r, echo=FALSE}

# Combine the two Pekel sets

pk_b$pk_type <- "buffered"
pk_u$pk_type <- "unbuffered"

pk <- rbind(pk_b, pk_u)

```


```{r, echo=FALSE, warning=FALSE, message=FALSE, include=FALSE}

# -------------------------------------------
# Stream gage - read in all gage info for CA
# ------------------------------------------

# Get general info about all gages in a given huc from NWIS
df <- fread(sprintf("https://waterservices.usgs.gov/nwis/site/?format=rdb&huc=%s&seriesCatalogOutput=true&siteStatus=all&hasDataTypeCd=dv,aw", huc_num), check.names = FALSE, header=TRUE)
g <- df
```


```{r, echo=FALSE, warning=FALSE,message=FALSE}

# ------------------------------------------------
# Stream gage - set criteria for gage selection
# ------------------------------------------------

# Format dates of data retrieval
g$begin_date <- as.Date(g$begin_date, format = "%Y-%m-%d")
g$end_date <- as.Date(g$end_date, format = "%Y-%m-%d")

# Get gages that have an end date in the 21st century
g.sub <- subset(g, end_date > "2010-01-01")

# Calculate the amt of active time for each gage
g.sub$time_active <- g.sub$end_date - g.sub$begin_date

# site_no needs to be a number
g.sub$site_no <- as.numeric(g.sub$site_no)

# Check if there are > 10 sites (url can't take > 10 at a time) ## no longer necessary since we're grabbing individual sites
sites <- unique(g.sub$site_no)

# Make sure site names have 8 characters; others aren't recognized in the automatic retrieval URL
sites <- subset(sites, nchar(sites) == 8)


```


```{r, echo=FALSE, warning=FALSE, message=FALSE, include=FALSE}

# ---------------------------------------------
# Stream gage - get data from selected sites
# --------------------------------------------

# Set up holder for all site info  
sg <- data.frame()

# Get monthly info from identified stream gages
for (site in sites) {

  file.next <- fread(sprintf("https://waterservices.usgs.gov/nwis/stat/?format=rdb&sites=%s&statReportType=monthly&statTypeCd=all&missingData=on", site), check.names = FALSE, header=TRUE)

  # Ignore no-data files, which start with #
  if (file.next[1, 1] != "#") {
      sg <- rbind(sg, file.next)
  }
}  

sg_orig <- sg
```


```{r, echo=FALSE, warning=FALSE, message=FALSE}

# Data type values are defined here: https://waterservices.usgs.gov/rest/Site-Service.html#outputDataTypeCd
# 00060 = discharge (cu ft/s)
# 00065 = gage height (ft)

# ---------------------------------------
# Stream gage - process aggregated info
# ---------------------------------------

# Remove sites in which the site# isn't valid
sg <- sg[sg$site_no %in% sites,]

# Create date from year and month columns
sg$date <- as.Date(with(sg, sprintf("%s-%02s-01", year_nu, month_nu)), "%Y-%m-%d")

# Remove dates prior to 1984 and past Pekel data
sg <- subset(sg, year_nu > 1983 & date < max(pk$date))

# Make sure values aren't characters
sg$mean_va <- as.numeric(sg$mean_va)

# Pare down dataset. This requires making sure sg is a data frame
sg <- data.frame(sg)
cols_to_keep <- c("site_no", "parameter_cd", "mean_va", "date")
sg <- sg[, cols_to_keep]

# Restrict to gage height or discharge info only
sg <- subset(sg, parameter_cd == '00065' | parameter_cd == "00060")

# Replace parameter info
sg[sg$parameter_cd=="00060", "parameter_cd"] <- "discharge"
sg[sg$parameter_cd=="00065", "parameter_cd"] <- "gage ht"

```
#####**Correlation table**

Querying NWIS for monthly stream gage data and correlating with Pekel data (kendall tau) yields:

```{r,echo=FALSE, warning=FALSE}

# -------------------------
# Stream gage and Pekel
# -------------------------

# Merge Pekel data and gage data
pk_sg <- merge(pk, sg, by = "date")

# Full data set
cor_psg <- pk_sg %>% 
  group_by(site_no, pk_type, parameter_cd) %>% 
  summarize(cor=cor(water, mean_va, use = "pairwise.complete.obs", method = "pearson"))

#cor_psg <- cor_psg[order(-cor_psg$cor),]

cor_psg %>% kable(col.names = c("Gage", "Pekel data", "Parameter", "r")) %>% kable_styling(bootstrap_options = "striped", full_width = FALSE)

```
Take-away points:  

* Buffered data typically have a higher correlation value than unbuffered
* Hard to generalize height vs. discharge strengths since only 1 gage has height info


#####**Using highest correlation to fit data**  

In this case, the highest correlation is:

```{r,echo=FALSE}

# Take max correlation to get relationship coefficients

# Max correlation row
max_cor <- as.data.frame(cor_psg) %>% 
            slice(which.max(cor))

```
`r kable(col.names = c("Gage", "Pekel data", "Parameter", "r"), max_cor) %>% kable_styling(full_width=FALSE)`  
*Linear fit*

```{r,echo=FALSE}
# Subset df using relevant metrics
siteno <- max_cor$site_no
pktype <- max_cor$pk_type
parametercd <- max_cor$parameter_cd
pk_sg.sub1 <- subset(pk_sg, site_no == siteno & pk_type==pktype & parameter_cd==parametercd) 

# Aaand...fit!
fit1 <- lm(water ~ mean_va, data = pk_sg.sub1) # poly(mean_va, 2)
summary(fit1)

# Get fit coefficients
b1 <- summary(fit1)$coefficients[1,1]
m1 <- summary(fit1)$coefficients[2,1]

```
*Associated plot*

```{r, echo=FALSE, warning=FALSE}
ggplot(pk_sg.sub1, aes(mean_va, water)) + 
  geom_point() +
  geom_smooth(method = "lm", color = "red", se = F) + 
              #, formula=y~poly(x, 2, raw=TRUE)) +
  theme_bw() +
  xlab(bquote('Discharge ('~ft^3~s^-1*')')) +
  ylab(bquote('Pekel water extent ('~km^2*')'))

```
All discharge data in this HUC show this heavy weighting at the lower end of the scale.

Missing Pekel data water values are replaced with the equation   

$y = `r b1` + `r m1`x_i$  


#####**Gage height data**  

In contrast, the gage height data have a more normal distribution.

*Linear fit*
```{r,echo=FALSE}

# get relationship coefficients for 'gage height, buffered'

# Subset df using relevant metrics
siteno <- "11450000"
pktype <- "buffered"
parametercd <- "gage ht"
pk_sg.sub2 <- subset(pk_sg, site_no == siteno & pk_type==pktype & parameter_cd==parametercd)

# Aaand...fit!
fit2 <- lm(water ~ mean_va, data = pk_sg.sub2)
summary(fit2)

# Get fit coefficients
b2 <- summary(fit2)$coefficients[1,1]
m2 <- summary(fit2)$coefficients[2,1]

```
*Associated plot*


```{r, echo=FALSE, warning=FALSE}
ggplot(pk_sg.sub2, aes(mean_va, water)) + 
  geom_point() +
  geom_smooth(method = "lm", color = "red", se = F) + 
  theme_bw() +
  xlab('Gage height (ft)') +
  ylab(bquote('Pekel water extent ('~km^2*')'))

```
Replace missing Pekel data water values with the equation

$y = `r b2` + `r m2`x_i$  



```{r, echo=FALSE}

# Replace values: discharge
pk_sg.sub1$db <- 0
pk_sg.sub1[which(is.na(pk_sg.sub1$water)), 'db'] <- NA
pk_sg.sub1[which(is.na(pk_sg.sub1$water)), 'water'] <- pk_sg.sub1[which(is.na(pk_sg.sub1$water)), 'mean_va']*m1 + b1

# Replace values: gage height
pk_sg.sub2$db <- 0
pk_sg.sub2[which(is.na(pk_sg.sub2$water)), 'db'] <- NA
pk_sg.sub2[which(is.na(pk_sg.sub2$water)), 'water'] <- pk_sg.sub2[which(is.na(pk_sg.sub2$water)), 'mean_va']*m2 + b2

# Combine the two subsets: 1 discharge, 1 gage height
pk_sg.sub <- rbind(pk_sg.sub1, pk_sg.sub2)

# Set factors
pk_sg.sub$pk_type <- as.factor(pk_sg.sub$pk_type)
pk_sg.sub$parameter_cd <- as.factor(pk_sg.sub$parameter_cd)
pk_sg.sub$huc8 <- as.factor(pk_sg.sub$huc8)
pk_sg.sub$site_no <- as.factor(pk_sg.sub$site_no)

# Reserve the original subset 2 for later
pk_sg.sub.nas <- pk_sg.sub

# Ensure that the values that were estimated are rolled back to NAs in the "original" database
pk_sg.sub.nas[is.na(pk_sg.sub.nas$db), 'water'] <- NA
pk_sg.sub.nas$db <- 'original'
pk_sg.sub$db <- "estimated"

# Combine
pk_sg.all <- rbind(pk_sg.sub, pk_sg.sub.nas)

```

```{r, warning=FALSE, echo=FALSE}

p <- ggplot(pk_sg.all, aes(date, water, color = as.factor(parameter_cd))) + 
  geom_line(size = 0.8) +
  scale_color_manual("Parameter", values = c("steelblue2", "blue")) +
  theme_bw() +
  xlab("Date") +
  ylab("Discharge") +
  geom_line(data=pk_sg.all, aes(date, water, linetype = db), color = c("black", "blue"), size = c(0.72, 0.8)) +
  scale_shape_manual("Pekel", values = c(1, 16), labels = c("Estimated", "Original")) + 
  scale_linetype_manual("Pekel", values = c("dotted", "solid"), labels = c("Estimated", "Original"))

p


```




```{r, warning=FALSE, echo=FALSE}

p <- ggplot(subset(pk_sg.all, site_no == siteno), aes(date, mean_va, color = as.factor(site_no))) + 
  geom_line(size = 0.8) +
  scale_color_manual("Stream gage", values = c("steelblue2")) +
  theme_bw() +
  xlab("Date") +
  ylab("Discharge") +
  geom_line(data=subset(pk_sg.all, parameter_cd == "gage ht"), aes(date, water, linetype = db), color = "black", size = 0.72) +
  scale_shape_manual("Pekel", values = c(1, 16), labels = c("Estimated", "Original")) + 
  scale_linetype_manual("Pekel", values = c("dotted", "solid"), labels = c("Estimated", "Original"))

p


```



