---
title: "HUC8 stream gage/Pekel data comparison"
output: html_notebook
fontsize: 9
editor_options: 
  chunk_output_type: inline
---

```{r setup, echo = FALSE, include=FALSE}
library(ggplot2)
library(reshape2) # for reshaping data format
library(dplyr) # for correlations by factor
library(knitr) # for formatting tables, BUT doensn't seem to work unless knitting
```
### Overview
This document describes leveraging the correlation between monthly stream gage discharge data (ft<sup>3</sup>/s) and Pekel monthly surface water data in order to fill gaps in the Pekel data record.

Stream gage information is from **HUC8 18040008 Upper Merced** (https://waterdata.usgs.gov/nwis/). Volume streamflow discharge data from all gages with complete records from 2006 through 2015 (3 of 22 listed gages) were output to individual *.csv files and merged with Pekel data. The consolidated file is accessed on Google drive through its URL:
```{r, warning=FALSE}
data_url = "1M6P5RJqgTxdazxjJMakKU6qdrBeLwvYr" #1t6XaZANrVRMShni8Xo_0Ok7esSM2vqBt"
df <- read.csv(sprintf("https://docs.google.com/uc?id=%s&export=download", data_url))
```


```{r, echo=FALSE, warning=FALSE, include=FALSE}
# Get rid of extraneous columns before reshaping
x <- df
x$date <- as.Date(with(x, sprintf("%d-%02d-01", year, month)), "%Y-%m-%d")
cols_to_keep <- c("date", "water", "sg_11264500", "sg_11266500", "sg_11270900")
x <- x[, cols_to_keep]

```   
<br>

```{r, echo=FALSE}
# Lag Pekel water data by 1 month
x <- x %>% mutate(lag.water = dplyr::lead(water, n=1, default = NA))

# Reformat data to long format for plotting. First reshape the gage data--
x.long <- melt(x, id.vars = c("water", "date", "lag.water"), variable.name = "gage", value.name = "discharge")

# Then the pekel data -- obsolete since we took out everything but Pekel water data
#x.long <- melt(x.long, id.vars = c("date", "gage", "discharge", "lag.value"), variable.name = "pekel")

```
Plotting individual stream gage data together with Pekel data yields the following.  Pekel data are in areal units, but have been scaled for display purposes.

```{r, warning=FALSE, echo=FALSE}
ggplot(x.long, aes(date, discharge, group = gage, color = gage)) + 
  geom_point() + 
  geom_line() +
  theme_bw() +
  xlab("Date") +
  ylab(bquote('Discharge ('~ft^3~s^-1*')')) +
  scale_color_discrete(name = "Stream gage", labels = c("11264500", "11266500", "11270900")) +
  
  # Force Pekel legend to appear by including a manufactured category in aes (here, gage[1])
  geom_line(data=x.long, aes(date, water*1000000, linetype = gage[1]), color = "black", size = 1.3) +
  scale_linetype_manual(name = "Pekel", values = ("solid"), labels = ("Water extent"))

```
Pekel peak values appear to slightly lag stream gage peaks, so summarize correlations by non-lagged and 1-month lagged dates.
<br>
Non-lagged correlations
```{r, echo=FALSE, warning=FALSE}

# Calculate non-lagged correlation
cor.nonlagged <- x.long %>%
 # filter(pekel == "water") %>%  
  group_by(gage) %>%
  summarize(COR = cor(discharge, water, use = "complete.obs"))
kable(cor.nonlagged, caption = "Non-lagged correlations")
```
1-month lagged correlations
```{r, echo=FALSE, warning=FALSE}
# Calculate lagged correlation
cor.lagged <- x.long %>%
  group_by(gage) %>%
  summarize(COR = cor(discharge, lag.water, use = "complete.obs"))
kable(cor.lagged, caption = "1-month lagged correlations")
```

```{r, echo = FALSE, warning = FALSE}
p <- ggplot(x, aes(sg_11270900, lag.water)) + 
     geom_point() + 
     theme_bw() +
     xlab(bquote('Stream gage discharge ('~ft^3~s^-1*')')) +
     ylab('Pekel monthly water') +
     geom_smooth(method = "lm", se = FALSE, color = "red")
p
```
The best correlation (sg_11270900) is relatively linear until ~2900 ft<sup>3</sup>/s. Restricting the stream gage data range to that value yields a higher correlation:

```{r, echo=FALSE}
max.discharge <- 2900
x.sub <- subset(x, sg_11270900 <= max.discharge)
cor(x.sub$sg_11270900, x.sub$lag.water, use = "complete.obs")
```

```{r, echo = FALSE, warning = FALSE}
ggplot(x.sub, aes(sg_11270900, lag.water)) + 
  geom_point() + 
  theme_bw() +
  xlab(bquote('Stream gage discharge ('~ft^3~s^-1*')')) +
  ylab('Pekel monthly water') +
  geom_smooth(method = "lm", se = FALSE, color = "red")
```
Calculate the linear equation of the fit
```{r, echo=FALSE}
fit <- lm(lag.water ~ sg_11270900, data = x.sub)
summary(fit)
```

```{r, echo = FALSE}
# assign coefficients from lm summary
b <- summary(fit)$coefficients[1,1]
m <- summary(fit)$coefficients[2,1]
```

and replace missing Pekel data water values with the resulting equation

$y = `r b` + `r m`x_i$

```{r, echo = FALSE}
# Get rid of all other gages

x.long <- subset(x.long, gage == 'sg_11270900')

# save a df as original data

x.original <- x.long


x.long[which(is.na(x.long$lag.water)), 'lag.water'] <- x.long[which(is.na(x.long$lag.water)), 'discharge']*m + b

# That established the values according to the lagged correlation.  Now unlag for plotting
# purposes.
x.long <-
 x.long %>% 
  mutate(water = dplyr::lag(lag.water, n=1, default = NA))

x.original$db <- "original"
x.long$db <- "estimated"

x.combined <- rbind(x.original, x.long)

```

where x = stream gage value. The resulting plot shows how the estimated data fill gaps in the Pekel record:

```{r, warning=FALSE, echo=FALSE}

p <- 
  ggplot(subset(x.combined, gage == "sg_11270900"), aes(date, discharge, color = gage)) + 
  geom_point() + 
  geom_line(size = 0.6) +
  scale_color_manual("Stream gage", values = c("steelblue2")) +
  theme_bw() +
  xlab("Date") +
  ylab(bquote('Discharge ('~ft^3~s^-1*')')) +
  #geom_point(data=x.combined, aes(date, water*1000000, shape = db), size = 1.0, color = "black") +
  geom_line(data=x.combined, aes(date, water*1000000, linetype = db), size = 0.9, color = "black") +
  scale_shape_manual("Pekel", values = c(1, 16), labels = c("Estimated", "Original")) + 
  scale_linetype_manual("Pekel", values = c("dotted", "solid"), labels = c("Estimated", "Original"))
p

```
