---
title: "HUC8 stream gage/Pekel/DSWE data comparison"
output: html_notebook
fontsize: 9
editor_options: 
  chunk_output_type: inline
---

```{r setup, echo = FALSE, include=FALSE}
library(ggplot2)
library(reshape2) # for reshaping data format
library(dplyr) # for correlations by factor
library(knitr) # for formatting tables, BUT doensn't seem to work unless knitting
```
### Overview
This document describes the comparison of monthly stream gage discharge data (ft<sup>3</sup>/s) with two imagery-derived water extents: Global Surface Water monthly water data (Pekel et al.) and monthly maximum surface water extents (Dynamic Surface Water Extent [Jones et al.; DSWE]).

Stream gage information is from **HUC8 18040008 Upper Merced** (https://waterdata.usgs.gov/nwis/). Volume streamflow discharge data from all gages with complete records from 2006 through 2015 (3 of 22 listed gages) were output to individual *.csv files and merged with Pekel data. The consolidated file is accessed on Google drive through its URL:
```{r, warning=FALSE}
# PEKEL
data_url = "1M6P5RJqgTxdazxjJMakKU6qdrBeLwvYr" #1t6XaZANrVRMShni8Xo_0Ok7esSM2vqBt"
df <- read.csv(sprintf("https://docs.google.com/uc?id=%s&export=download", data_url))
```


```{r, echo=FALSE, warning=FALSE, include=FALSE}
# Pekel

# Get rid of extraneous columns before reshaping
x <- df
x$date <- as.Date(with(x, sprintf("%d-%02d-01", year, month)), "%Y-%m-%d")
cols_to_keep <- c("date", "water_gee", "sg_11264500", "sg_11266500", "sg_11270900")
x <- x[, cols_to_keep]
x$water_gee <- x$water_gee * 0.0009  # convert from # of pixels to km^2: 900 m^2/pixel x 1e-06 km^2/m^2
colnames(x)[colnames(x)=="water_gee"] <- "pekel"

```   
<br>

```{r, echo=FALSE}
# PEKEL
# Lag Pekel water data by 1 month
x <- x %>% mutate(lag.pekel = dplyr::lead(pekel, n=1, default = NA))

# Reformat data to long format for plotting. First reshape the gage data--
x.long <- melt(x, id.vars = c("pekel", "date", "lag.pekel"), variable.name = "gage", value.name = "discharge")

```

```{r, warning=FALSE}
# DSWE

#https://drive.google.com/open?id=1uPRWSMCoMXX_R7QRPUuNOkUvziDq8rhj
data_url = "1uPRWSMCoMXX_R7QRPUuNOkUvziDq8rhj"
df2 <- read.csv(sprintf("https://docs.google.com/uc?id=%s&export=download", data_url))
```

```{r, echo=FALSE}
# DSWE
x2 <- df2
x2$date <- substring(x2$date, 7,12) # Extract date
x2$date <- as.Date(paste0(as.character(x2$date), '01'), format='%Y%m%d') #Set date to month

# Remove extraneous columns
cols_to_keep <- c("date", "X1", "X2", "X3")
x2 <- x2[, cols_to_keep]

# Remove extraneous row
x2 <- x2[-1, ]

```

```{r, echo=FALSE}
# Lag DSWE water data by 1 month
x2$sum <- x2$X1 #+ x2$X2 + 0.5*x2$X3
x2 <- x2 %>% mutate(lag.sum = dplyr::lead(sum, n=1, default = NA))
x2.long <- melt(x2, id.vars = "date", variable.name = "dswe_class", value.name = "dswe_val")
x2.long$dswe_val <- x2.long$dswe_val/1000

# put in mock gage class
x2.long$gage <- "none"
```

Plotting individual stream gage data together with Pekel data yields the following.  Pekel data are in areal units, but have been scaled for display purposes.

```{r, warning=FALSE, echo=FALSE}
ggplot(subset(x.long, gage == "sg_11270900"), aes(date, discharge, group = gage, color = gage)) + 
 # geom_point() + 
  geom_line() +
  theme_bw() +
  xlab("Date") +
  ylab(bquote('Discharge ('~ft^3~s^-1*')')) +
  scale_color_discrete(name = "Stream gage", labels = c("11264500", "11266500", "11270900")) +

  # Force Pekel legend to appear by including a manufactured category in aes (here, gage[1])
  geom_line(data=x.long, aes(date, pekel*100, linetype = gage[1]), color = "black", size = 1.3) +
  scale_linetype_manual(name = "Pekel", values = ("solid"), labels = ("Pekel water extent")) +
  
  # DSWE data
  geom_line(data=subset(x2.long, dswe_class == "sum" & date > "2005-01-01" & date < "2016-01-01"), aes(date, dswe_val*10, size = gage[1]), color = "purple") +
  scale_size_manual(name = "DSWE", values = (0.9), labels = "DSWE water extent")

```



```{r}

#chunks:
x2.long$gage <- NULL # take gage back out

test <- merge(x.long, x2.long, by = "date")

cor_all <- test %>% group_by(dswe_class) %>% summarize(cor=cor(discharge, dswe_val, use = "complete.obs"))

cor_all <- test %>% group_by(dswe_class, gage) %>% summarize(cor=cor(discharge, dswe_val, use = "complete.obs"))

cor_all <- test %>% group_by(gage) %>% summarize(cor=cor(discharge, pekel, use = "complete.obs"))

test.sub <- subset(test, date > "2005-01-01" & date < "2016-01-01" & gage == "sg_11264500" & dswe_class!= "lag.sum")

ggplot(test.sub, aes(date, dswe_val, group = dswe_class, color = dswe_class)) + geom_line() + geom_point() + geom_line(data=test.sub, aes(date, lag.pekel*10), color = "black", size = 1.2)
```

