---
title: 
output: html_notebook
---
### Exploration of Pekel/Washington data
```{r, echo=FALSE, warning = FALSE}
library(dplyr)  #filter
library(Kendall)
#path.in <- "D:/projects/floods/data"
#file <- "Pekel_LCMAP_Washington_By_County_jjw.csv"
```
Access file hosted on Google drive through its URL
```{r}
data_url = "1O5a7d9RSnaPU0OsoXBS0YNR8xURy5e9W"
df <- read.csv(sprintf("https://docs.google.com/uc?id=%s&export=download", data_url))
```

```{r, echo=FALSE}

x <- df
# Calculate Mann Kendall
mk <- by(x$pct_water_in_dev, x$county, function(y) MannKendall(y))

# Grab all p values
p.vals <- sapply(mk, function(y) {as.numeric(y)[[2]]})

# Transform to data frame
p.vals.df <- stack(p.vals)

# Significant ones only.
p.threshold1 <- 0.005
mk.sig <- p.vals.df %>%
  filter(values < p.threshold1) 

```
Counties with significant (p < **`r p.threshold1`**) trends in 'percent water in developed' using Mann Kendall.
```{r, echo=FALSE}

x.sub <- x %>%
  filter(county %in% mk.sig$ind)

p <- ggplot(x.sub, aes(year, log10(pct_water_in_dev), group = county)) + geom_line(aes(color=county)) +
  theme_bw()


p
```
```{r, echo=FALSE}

x <- df
# Calculate Mann Kendall
mk <- by(x$pct_devt_under_water, x$county, function(y) MannKendall(y))

# Grab all p values
p.vals <- sapply(mk, function(y) {as.numeric(y)[[2]]})

# Transform to data frame
p.vals.df <- stack(p.vals)

# Significant ones only
p.threshold2 <- 0.05
mk.sig <- p.vals.df %>%
  filter(values < p.threshold2) 

```

Counties with significant (p < **`r p.threshold2`**) trends in 'percent developed under water' using Mann Kendall.
```{r, echo=FALSE}

x.sub <- x %>%
  filter(county %in% mk.sig$ind)

p <- ggplot(x.sub, aes(year, log10(pct_devt_under_water), group = county)) + geom_line(aes(color=county)) +
  theme_bw()

p
```



```{r, echo=FALSE, include = FALSE}
# sitesmap2.R
# Map the sites data using the leaflet package.
# This creates a prettier, interactive map.
library(leaflet)
library(maps)
library(htmlwidgets) # To save the map as a web page.
```

```{r, echo=FALSE, include=FALSE, eval=FALSE}
# The data to map.
# State boundaries from the maps package. The fill option must be TRUE.
bounds <- map('county', 'Washington', fill=TRUE, col= 'lightblue')

# Get only the significant counties
bounds2 <- lapply(bounds, function(y) {y[c(14,16, 24, 32, 34, 39)]})


my.map <- leaflet(bounds) %>%
  addTiles(urlTemplate = 
             "http://{s}.basemaps.cartocdn.com/light_all/{z}/{x}/{y}.png") %>%
  addMarkers(lng = -123.3040, lat= 47.7425, popup = "Jefferson")
my.map

#invisible(print(map))

```