---
title: "Pixel-based time series water analysis"
fontsize: 9
output: html_notebook
editor_options:
  chunk_output_type: inline
---


####Overview
This script creates a vectorized tiff indictating whether a pixel was water for any month.
Chris Konrad 2019
Cosmetic modifications JWalker June 2019

####Input
Monthly surface water tiffs in which class 0 = No Data, class 1 = No Water, and class 2 = Water

####Output
  - 4-column array with row/column of pixel; month (as time step); and classification (water/non)
  - Individual files with pixel coordinates and water/no water status

```{r, echo = FALSE, warning = FALSE, message = FALSE}

# ---------------------------------------------------------------------- #
#### General setup ####
# ---------------------------------------------------------------------- #

# Paths
path_data <- 'E:/projects/place/R/timeseries'
path_tifs <- 'E:/projects/place/data/tifs'
setwd(path_tifs)

# Load packages in a way that's easy for others to as well
load_packages <- function(pkgs){
  for (pkg in pkgs){
    #  require returns TRUE invisibly if it was able to load package
    if(!require(pkg, character.only = TRUE)){
      #  If package was not able to load, re-install
      install.packages(pkg, dependencies = TRUE)
      #  Load package after installing
      require(pkg, character.only = TRUE)
    }
  }
}

# Load packages
load_packages(c("abind", 
                "sp", 
                'raster',
                'rgdal',  #v1.4-4
                'tictoc'))
```

```{r, echo = FALSE}

# ---------------------------------------------------------------------- #
#### General info ####
# ---------------------------------------------------------------------- #

allhucs <- c('18020003')

coords_huc <- data.frame(huc = character(),
                         lon = numeric(),
                         lat = numeric())

# Constants
yr_start <- 1985
yr_end <- 2015
yrs <- seq(yr_start, yr_end)
mm <- c('01','02','03','04','05','06','07','08','09','10','11','12') #c(paste0('0', seq(1, 9)), seq(10, 12))
nts <- 370 # Number of months in time series
np <- NA # Number of pixels

# Sequential list of all months padded with zeros to 3 digits (e.g., '001')
ts_labels <- sprintf("%03d", seq(1:(12 * (yr_end - (yr_start - 1)))))

```


```{r, echo=FALSE, warning = FALSE}

# ---------------------------------------------------------------------- #
#### Process each HUC ####
# ---------------------------------------------------------------------- #

#SURFACE WATER TIME SERIES FROM 1985-01 to 2015-10, TIF FOR 2013-06 IS BAD
for (h in 1:length(allhucs)) {
  
#process_hucs <- function(huc) {  # not sure why this wouldn't work
  
  huc <- allhucs[h]
  tic('loop for huc')
  
# Generate filenames for each month/year combination (e.g. '18020002/monthly_water_1985_01_18020002.tif') to import files
  filenames <- sapply(yrs, function(y) sapply(mm, function(m) paste0(huc, '/monthly_water_', y, '_', m, '_', huc, '.tif')))
  filenames <- filenames[1:nts] # This indexing only works as long as the first year is complete and the last is incomplete
  filenames <- filenames[-342] # BAD TIFF!
  
# Generate matching year/month array (e.g. '1985_01') as rownames
  yr_mn <- sapply(yrs, function(y) sapply(mm, function(m) paste0(y, '_', m)) ) # generate labels
  yr_mn <- yr_mn[1:nts]
  yr_mn <- yr_mn[-342]
  
# Generate array with number of dry/wet pixels in each month
  ts_sum <- array(NA, dim = c(0, 3)) 

# Generate tif index with row and column indices for vectorized tiff
# Pixel order: row 1 col 1, 2, ...n; row 2 col 1, 2, ...n; ... 
#  rasters <- lapply(file.path(path_tifs, filenames), raster) # bombs otherwise
  tmp <- raster(file.path(path_tifs, filenames[1]))
  nr <- dim(tmp)[[1]] 
  nc <- dim(tmp)[[2]]
  
  tiff_index <- rep(c(1:nr), nc)
  tiff_index <- sort(tiff_index) # sorts rows into 1,1,..,1,2,2...2,...
  tiff_index <- cbind(tiff_index, rep(c(1:nc), nr))

# Get LL corner coordinates
  coords_huc <- rbind(coords_huc, c(huc, extent(tmp)[1], extent(tmp)[3]))
  
# Vectorize raster
  tmp <- as.vector(tmp)  
  np <- sum(!is.na(tmp)) # number of actual data values

# Create logical vector showing whether a pixel had water in any month to ID pixels to model
# If binary vector is TRUE OR any of the other vectors == 2, that spot gets a TRUE for water
# **Tried to unloop/sapply but bombs due to data volume**
  water_any_ts <- (tmp == 2)  # 2 is the water class
  for (ts in 2:length(filenames)) {
      water_any_ts <<- (water_any_ts | (as.vector(raster(file.path(path_tifs, filenames[ts]))) == 2))
  }

# Vectorize tiffs and compile in tmp: rows are pixels; cols are raster rows/cols/ts code/classification code
  for (ts in 1:length(filenames)) {
       tmp <- cbind(tiff_index, ts, as.vector(raster(file.path(path_tifs, filenames[ts])))) 
       tmp[tmp[, 4] == 0] <- NA # Change code 0 to NA 
       tmp[!water_any_ts, 4] <- NA # Change any non-water pixels to NA
       tmp <- tmp[complete.cases(tmp), ] # Remove rows (pixels) that were dry in that month

# Array with time-series of wet/dry (cols) for each pixel (row): tsXXX where XXX is serial code for month from 001 to 370
       assign(paste0('ts', ts_labels[ts]), tmp, envir = .GlobalEnv)

# ts_sum summarizes results for each month in rows
# Columns: # of unclassified pixels in HUC, # of dry pixels, and # of wet pixels
# ** Replication of what we aggregate through GEE **
       tmp1 <- sum(tmp[, 4] == 1, na.rm = TRUE)
       tmp2 <- sum(tmp[, 4] == 2, na.rm = TRUE)
       ts_sum <- rbind(ts_sum, c(np - tmp1 - tmp2, tmp1, tmp2))

  } # Close ts loop

# Set coordinate df names 
 names(coords_huc) <- c("huc", "lon", "lat")

# Set rownames as year/month
 dimnames(ts_sum)[[1]] <- yr_mn
  
# Clean up 
 rm(tmp, tmp1, tmp2, ts)  #mm, nts

# Create directory for timeseries
 dir.create(file.path(path_data, huc))
 
# Save data to Rdata file 
 save.image(file.path(path_data, huc, paste0('ts_array_', huc, '.Rdata')))

# Write out data
 write(paste0('*** Completed HUC ', huc), '')
  
} # Close HUC loop





```


```{r, echo = FALSE, warning=FALSE}

#sapply(allhucs, function(x) process_hucs(x))

rm(mm, nts)
toc()

```



#  c(-121.583291, 40.812260), #HUC 18020002
#  c(-122.370214, 40.45194)) #HUC18030003